### 2024-11-03 paper/paper.qmd
Survey

---
title: "Forecasting the 2024 U.S. Presidential Election"
subtitle: "My subtitle if needed"
author: 
  - Jason Yang
  - Another author
thanks: "Code and data are available at: [https://github.com/Jerryx2020/US_election_prediction/tree/main]."
date: "`r format(Sys.Date() - 1, '%A, %B %d, %Y')`" #chatgpt assisted how to create a custom date for due date November 4
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Idealized Methodology

In designing a forecast for the upcoming US presidential election with a $100,000 budget, our methodology focuses on creating a representative survey that captures the voting intentions of likely voters across the United States. The objective is to gather reliable, high-quality data that supports a well-informed forecast through effective sampling, data validation, and aggregation techniques.

Our target population is voters aged 18 and above, with a sample size of approximately 10,000 responses, 200 responses from each state, to ensure a statistically significance at the national level and within key demographic groups. To achieve balanced representation, we will employ stratified random sampling based on age, gender, race/ethnicity, education, region, and urban/rural status. This approach will involve weighting responses using recent census data and voter turnout statistics to address any demographic discrepancies.

For recruitment, we will combine online survey panels, social media outreach, and targeted telephone recruitment. These methods are chosen to increase accessibility for harder-to-reach demographics, such as older adults and rural residents. To encourage participation, we will offer modest incentives, such as a small monetary compensation or entry into a prize draw. All data collection will be conducted through a reliable survey platform—Google Forms.

The survey itself will be concise and straightforward, focusing on voting intentions, key issues, and demographic information. For data validation, in the survey, we will include attention-check questions as respondents are very likely to complete the form for an entry into a prize draw. We will also conduct multiple waves of the survey, we will adopt a "poll-of-polls" approach, aggregating responses from different waves while applying weights based on relevance.

To mitigate biases such as non-response bias, social desirability bias, and order bias, our team will implement several strategies. We will send reminders to non-respondents to encourage participation, emphasizing the prize draw incentives to increase response rates. Survey questions will be carefully crafted to maintain neutral wording and avoid sensitive topics that might discourage honest responses. Additionally, within each wave of polls, we will randomize the order of questions to minimize the impact of question order on responses. These measures aim to enhance the reliability and accuracy of our survey results.

Ethically, our approach prioritizes respondent privacy and data security. We will ensure that participants’ responses remain anonymous and that all data is handled securely. Transparency is also essential; respondents will be informed about the survey’s sponsorship, methodology, and data use

The survey will be implemented on Google Forms, with a link provided in the appendix. We also included the questions in the appendix for better understandings.

## Idealized Survey

The proposed survey is designed using Google Forms,https://docs.google.com/forms/d/e/1FAIpQLSeHHeKaryNQ6sKgbuOH-ZgXwQYkNw9jBdxIbgeXWVj_t1ob2w/viewform?usp=sf_link

## Survey Copy

1. **Who do you intend to vote for in the 2024 U.S. Presidential Election?**
  - Kamala Harris (Democratic Party)
  - Donald Trump (Republican Party)
  - Undecided 
  - Other:

2. **How certain are you about your choice?  **
  - Very Certain
  - Somewhat certain
  - Unsure

3. **Which of the following issues are most important in deciding your vote? (Select up to 3)**
  - Economy and jobs
  - Healthcare
  - Climate Change
  - Education
  - Immigration
  - National Security 
  - Social justice and Equality 
  - Abortion rights
  - Gun control
  - Other:

4. **What is your age?**
  - 18-24
  - 24-34
  - 35-44
  - 45-54
  - 55-64
  - 65 or older

5. **What is your gender?**
  - Male 
  - Female
  - Non-binary/Other
  - Prefer not to say

6. **What is your race/ethnicity? (Select all that apply)**
  - White
  - Black or African American 
  - Hispanic or Latino 
  - Asian
  - Native American or Alaska Native
  - Native Hawaiian or Other Pacific Islander 
  - Other:

7. **In which U.S. state do you currently reside**
  - ______________

8. **If you voted in 2020, who did you vote for?**
  - Joe Biden 
  - Donald Trump 
  - Other:

\newpage

# References

### 2024-11-03 paper/paper.qmd
Updated Abstract

@@
 title: "Forecasting the 2024 U.S. Presidential Election"
-subtitle: "My subtitle if needed"
 author: 
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This paper presents a multiple linear regression model and a bayesian model for forecasting the outcome of the 2024 U.S.
+Presidential Election.
+Using the data collected from high-quality polls from various pollsters, we generate these models by selecting relevant variables such as sample size, percentage support for each candidate, and sate.
+By comparing the predictive power of both models, we aim to provide a reliable forecast of the election outcome and a deeper understanding of public sentiment and polling reliability."
 format: pdf
@@
 
-The proposed survey is designed using Google Forms,https://docs.google.com/forms/d/e/1FAIpQLSeHHeKaryNQ6sKgbuOH-ZgXwQYkNw9jBdxIbgeXWVj_t1ob2w/viewform?usp=sf_link
+The proposed survey is designed using Google Forms,
+https://docs.google.com/forms/d/e/1FAIpQLSeHHeKaryNQ6sKgbuOH-ZgXwQYkNw9jBdxIbgeXWVj_t1ob2w/viewform?usp=sf_link
 

### 2024-11-04 paper/paper.qmd
Updated Model

@@
 library(tidyverse)
-library(palmerpenguins)
 ```
@@
 
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
+The dataset used for this analysis was sourced from FiveThirtyEight’s poll aggregation platform, which compiles high-quality polling data from various reputable pollsters across the U.S.
+(@fivethirtyeight).
+This analysis uses the statistical programming language R (@R) and various libraries for data manipulation and visualization, including tidyverse for efficient data wrangling and ggplot2 for creating insightful visualizations (@tidyverse, @ggplot2).
+By employing robust statistical methods and tools, this analysis seeks to forecast potential outcomes of the 2024 U.S.
+Presidential Election.
 
@@
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
-
 ## Outcome variables
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
-
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-Talk way more about it.
+In this analysis, the outcome variable of interest is the percentage of support a candidate receives in each poll, represented by pct.
+This variable indicates the proportion of respondents within a poll who favor a particular candidate, measured as a percentage.
+Given that pct serves as a continuous variable bounded between 0 and 100, it is well-suited for modeling the levels of support across different polls and over time.
 
@@
 
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+This analysis employs two predictive models to estimate the anticipated support for the two major candidates in the 2024 U.S.
+Presidential Election: a multiple linear regression model.
+These models use high-quality polling data from reputable sources, with relevant predictors to provide insights into public opinion trends.
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+The multiple linear regression model is designed to predict the candidate's percentage of support (pct) as a linear function of various predictors. Formally, we define the model as:
+
+\begin{align*}
+\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{sample\_size}_i + \beta_3 \cdot \text{transparency\_score}_i \\
+&\quad + \sum_{k=1}^{K} \delta_k \cdot \text{state}_{ik} + \beta_4 \cdot \text{end\_date}_i + \epsilon_i,
+\end{align*}
 

### 2024-11-04 scripts/03-clean_data.R

@@ -19,7 +19,7 @@ raw_data <- read_csv("data/01-raw_data/president_polls.csv") |>
 
 Analysis_data <- raw_data |> 
   filter(numeric_grade >= 3.0) %>% 
-  select(candidate_name, pollster, sample_size, end_date, numeric_grade, methodology, state, pct, pollscore) %>%
+  select(candidate_name, pollster, sample_size, end_date, numeric_grade, methodology, state, pct, pollscore, transparency_score, start_date) %>%
   mutate(
     end_date = mdy(end_date),
     state = if_else(is.na(state), "National", state)

### 2024-11-04 scripts/06-model_data.R

@@ -19,156 +19,37 @@ library(splines)
 library(here)
 
 #### Read data ####
-data <- read_csv("data/analysis_data/analysis_data.csv")
+data <- read_csv("data/02-analysis_data/analysis_data.csv")
 
-just_harris_high_quality <- read.csv("data/analysis_data/just_harris_high_quality.csv")
+just_harris_high_quality <- read.csv("data/02-analysis_data/just_harris_high_quality.csv")
 just_harris_high_quality <- just_harris_high_quality %>%
-  drop_na(end_date_num, pollster, state, sample_size)
+  drop_na(pollster, state, sample_size)
 
-#### Exploratory Data Visualization ####
-# Base plot for Harris polling percentage over time
-base_plot <- ggplot(just_harris_high_quality, aes(x = end_date, y = pct)) +
-  theme_classic() +
-  labs(y = "Harris Percent", x = "Date")
-
-# Plot the base data and apply smoothing
-base_plot + geom_point() + geom_smooth() +
-  ggtitle("Polling Estimates Over Time")
-
-# Plot colored by pollster
-base_plot + geom_point(aes(color = pollster)) + geom_smooth() +
-  theme(legend.position = "bottom") + ggtitle("Polling by Pollster")
-
-#### Bayesian Models ####
-# Convert 'pollster' and 'state' to factor variables for Bayesian models
 just_harris_high_quality <- just_harris_high_quality %>%
   mutate(
     pollster = factor(pollster),
-    state = factor(state)
+    state = factor(state),
+    methodology = factor(methodology),
+    numeric_grade = as.numeric(numeric_grade),
+    transparency_score = as.numeric(transparency_score),
+    sample_size = as.numeric(sample_size),
+    end_date = as.Date(end_date),
+    start_date = as.Date(start_date)
   )
 
-# Define priors
-priors <- normal(0, 2.5, autoscale = TRUE)
-
-# Bayesian Model 1: Random intercept for pollster
-model_formula_1 <- cbind(num_harris, sample_size - num_harris) ~ (1 | pollster)
-bayesian_model_1 <- stan_glmer(
-  formula = model_formula_1,
-  data = just_harris_high_quality,
-  family = binomial(link = "logit"),
-  prior = priors,
-  prior_intercept = priors,
-  seed = 123,
-  cores = 4,
-  adapt_delta = 0.99
-)
-
[…]

### 2024-11-04 paper/paper.qmd
Updated Model Descriptions

@@
 
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+- pct: The percentage of the vote or support that the candidate received in the poll (e.g., 51.0 for Kamala Harris, 48.0 for Donald Trump).
+- numeric_grade: A numeric rating given to the pollster to indicate their quality or reliability (e.g., 3.0).
+- sample_size: The total number of respondents participating in the poll (e.g., 2712).
+- transparency_score:A score reflecting the pollster’s transparency about their methodology (e.g., 9.0).
+"A grade for how transparent a pollster is, calculated based on how much information it discloses about its polls and weighted by recency.
+The highest Transparency Score is 10."
+- state: The U.S. state where the poll was conducted or focused, if applicable.
+- end_date: The date the poll ended (e.g., 10/11/24).
+- $\epsilon_i$: The error term for poll accounting for variability not explained by the predictors.
 

### 2024-11-04 paper/paper.qmd
Add Introduction for Pollster Analysis
Add Introduction for Pollster Analysis

@@
 
+# Pollster Analysis
+
+The Marquette Law School Poll employs a rigorous methodology to survey adults in the US on national issues, incorporating probability-based sampling that combines Address-Based Sampling (ABS) and Stratified Random Sampling.
+This approach, including online and offline respondents, ensures broad representativeness.
+The SSRS Polling Panel supports participant recruitment, and weighting adjustments enhance result accuracy.
+
+## What is the population, frame, and sample?
+
+## How is the sample recruited?
+
+## What sampling approach is taken, and what are some of the trade-offs of this?
+
+## How is non-response handled?
+
+## What is good and bad about the questionnaire?
+
 \newpage

### 2024-11-04 paper/paper.qmd
Explain Population, Frame and Sample of the Pollster
Explain Population, Frame and Sample of the Pollster

@@
 
+The population for the poll includes adults aged 18 and over across all 50 states and the District of Columbia.
+The sampling frame was constructed through ABS, leveraging the US Postal Service's Computerized Delivery Sequence (CDS), a comprehensive, regularly updated list of residential addresses.
+The primary source for participants is the SSRS Opinion Panel, which includes both ABS and telephone survey data to capture hard-to-reach demographics, like non-Internet users.
+The survey ultimately included 1,005 adults, including registered and likely voters, with weighted samples to ensure proportional representation.
+
 ## How is the sample recruited?

### 2024-11-04 paper/paper.qmd
How Sample Recruited
How Sample Recruited

@@
 
+Participants were recruited via the SSRS Omnibus Panel, a probability panel formed from ABS and telephone survey data.
+This dual approach ensured that both Internet and non-Internet users were included, minimizing online-only bias.
+Stratified by demographics (age, gender, race, education, region, and partisan affiliation), this process produced a balanced representation across groups.
+Selected participants received an email invitation with a unique link to the survey.
+Non-responders received up to two reminder emails, and those who opted for text notifications also received reminders.
+Participants received an e-gift card incentive upon survey completion.
+
 ## What sampling approach is taken, and what are some of the trade-offs of this?

### 2024-11-04 paper/paper.qmd
Sampling Approach taken in Pollster
Sampling Approach taken in Pollster

@@
 
+The Marquette Law School Poll combines ABS and stratified random sampling.
+The ABS covers all residential addresses using USPS delivery sequences, ensuring broad geographic reach.
+To include hard-to-reach demographics, SSRS supplements ABS data with telephone survey responses.
+Stratified sampling by key demographics (age, gender, race, education, region, and political party) ensures representation across major groups.
+This probability-based sampling minimizes bias but requires significant resources.
+Stratification and weighting to represent specific populations add to survey complexity and cost.
+
 ## How is non-response handled?

### 2024-11-04 paper/paper.qmd
Non-Response Handled in Pollster
Non-Response Handled in Pollster

@@
 
+To address non-response and improve representativeness, SSRS applies weighting adjustments based on demographic variables such as age, gender, race, education, region, and Internet use.
+This process aligns sample characteristics with adult population parameters, reducing bias from demographic differences in response rates.
+
 ## What is good and bad about the questionnaire?

### 2024-11-04 paper/paper.qmd
Good and Bad for Pollster
Good and Bad for Pollster

@@
 
+The questionnaire is well-designed, with a collaborative approach that reduces respondent burden and improves comprehension.
+A thoughtfully structured skip pattern enhances flow and minimizes dropout rates.
+The probability-based sampling, combined with extensive weighting and stratification, enables a representative sample of adults.
+However, heavy reliance on web-based responses may introduce Internet bias, potentially underrepresenting non-Internet households.
+Additionally, the questionnaire’s complexity may increase participant fatigue, affecting response completeness.
+The response rate of approximately 47.4% also indicates some level of attrition in the sample.
+
 \newpage

### 2024-11-04 paper/paper.qmd
Add Reference of Pollster
Add Reference of Pollster

@@
 
-The Marquette Law School Poll employs a rigorous methodology to survey adults in the US on national issues, incorporating probability-based sampling that combines Address-Based Sampling (ABS) and Stratified Random Sampling.
+The Marquette Law School Poll employs a rigorous methodology to survey adults in the US on national issues, incorporating probability-based sampling that combines Address-Based Sampling (ABS) and Stratified Random Sampling [@citemarquette].
 This approach, including online and offline respondents, ensures broad representativeness.
@@
 The sampling frame was constructed through ABS, leveraging the US Postal Service's Computerized Delivery Sequence (CDS), a comprehensive, regularly updated list of residential addresses.
-The primary source for participants is the SSRS Opinion Panel, which includes both ABS and telephone survey data to capture hard-to-reach demographics, like non-Internet users.
-The survey ultimately included 1,005 adults, including registered and likely voters, with weighted samples to ensure proportional representation.
+The primary source for participants is the SSRS Opinion Panel, which includes both ABS and telephone survey data to capture hard-to-reach demographics, like non-internet users.
+The survey ultimately included 1,005 adults, including registered and likely voters, with weighted samples to ensure proportional representation [@citemarquette].
 
@@
 Participants were recruited via the SSRS Omnibus Panel, a probability panel formed from ABS and telephone survey data.
-This dual approach ensured that both Internet and non-Internet users were included, minimizing online-only bias.
+This dual approach ensured that both internet and non-internet users were included, minimizing online-only bias.
 Stratified by demographics (age, gender, race, education, region, and partisan affiliation), this process produced a balanced representation across groups.
@@
 Non-responders received up to two reminder emails, and those who opted for text notifications also received reminders.
-Participants received an e-gift card incentive upon survey completion.
+Participants received an e-gift card incentive upon survey completion [@citemarquette].
 
@@
 To include hard-to-reach demographics, SSRS supplements ABS data with telephone survey responses.
-Stratified sampling by key demographics (age, gender, race, education, region, and political party) ensures representation across major groups.
+Stratified sampling by key demographics (age, gender, race, education, region, and political party) ensures representation across major groups [@citemarquette].
 This probability-based sampling minimizes bias but requires significant resources.
@@
 
-To address non-response and improve representativeness, SSRS applies weighting adjustments based on demographic variables such as age, gender, race, education, region, and Internet use.
+To address non-response and improve representativeness, SSRS applies weighting adjustments based on demographic variables such as age, gender, race, education, region, and internet use [@citemarquette].
 This process aligns sample characteristics with adult population parameters, reducing bias from demographic differences in response rates.
@@
 The probability-based sampling, combined with extensive weighting and stratification, enables a representative sample of adults.
-However, heavy reliance on web-based responses may introduce Internet bias, potentially underrepresenting non-Internet households.
+However, heavy reliance on web-based responses may introduce internet bias, potentially underrepresenting non-internet households.
 Additionally, the questionnaire’s complexity may increase participant fatigue, affecting response completeness.
-The response rate of approximately 47.4% also indicates some level of attrition in the sample.
+The response rate of approximately 47.4% also indicates some level of attrition in the sample [@citemarquette].
 

### 2024-11-04 scripts/03-clean_data.R
Updated Model

@@ -17,26 +17,32 @@ library(tidyverse)
 raw_data <- read_csv("data/01-raw_data/president_polls.csv") |>
   clean_names()
 
-Analysis_data <- raw_data |> 
-  filter(numeric_grade >= 3.0) %>% 
+Analysis_data <- raw_data  %>% 
   select(candidate_name, pollster, sample_size, end_date, numeric_grade, methodology, state, pct, pollscore, transparency_score, start_date) %>%
   mutate(
     end_date = mdy(end_date),
-    state = if_else(is.na(state), "National", state)
+    start_date = mdy(start_date)
   ) %>%
   filter(candidate_name %in% c("Donald Trump", "Kamala Harris"))
 
 Analysis_data <- Analysis_data %>%
   mutate(state = case_when(
     state == "Nebraska CD-2" ~ "Nebraska",
+    state == "Maine CD-1" ~ "Maine" , 
+    state == "Maine CD-2" ~ "Maine",
     TRUE ~ state  # Keeps all other values as they are
   ))
+
+Analysis_data <- Analysis_data %>% drop_na()
+
+Analysis_data <- Analysis_data %>% filter(numeric_grade >= 1)
 
 just_harris_high_quality <- Analysis_data |>
   filter(
     candidate_name == "Kamala Harris",
     end_date >= as.Date("2024-07-21"))  |> 
   mutate(
+    state = if_else(is.na(state), "National", state),
     num_harris = round((pct / 100) * sample_size, 0) 
   )
 

### 2024-11-04 scripts/06-model_data.R

@@ -22,13 +22,11 @@ library(here)
 data <- read_csv("data/02-analysis_data/analysis_data.csv")
 
 just_harris_high_quality <- read.csv("data/02-analysis_data/just_harris_high_quality.csv")
-just_harris_high_quality <- just_harris_high_quality %>%
-  drop_na(pollster, state, sample_size)
 
 just_harris_high_quality <- just_harris_high_quality %>%
   mutate(
-    pollster = factor(pollster),
-    state = factor(state),
+    pollster = as.factor(pollster),
+    state = as.factor(state),
     methodology = factor(methodology),
     numeric_grade = as.numeric(numeric_grade),
     transparency_score = as.numeric(transparency_score),
@@ -39,29 +37,13 @@ just_harris_high_quality <- just_harris_high_quality %>%
 
 
 linear_model <- lm(
-  pct ~ numeric_grade + sample_size + transparency_score + state + end_date, 
+  pct ~ pollscore + numeric_grade + sample_size + state + end_date, 
   data = just_harris_high_quality
 )
 
-summary(linear_model)
-
-just_harris_high_quality <- just_harris_high_quality %>%
-  mutate(predicted_pct = predict(linear_model, newdata = just_harris_high_quality))
-
-# Plot actual vs. predicted values
-ggplot(just_harris_high_quality, aes(x = end_date)) +
-  geom_point(aes(y = pct, color = "Actual")) +
-  geom_line(aes(y = predicted_pct, color = "Predicted")) +
-  labs(
-    y = "Polling Percentage (pct)",
-    x = "Days since Start",
-    title = "Actual vs. Predicted Polling Percentages for Kamala Harris",
-    color = "Legend"
-  ) +
-  theme_minimal()
-
 
 #### Save Key Results ####
+
 write_csv(just_harris_high_quality, "data/02-analysis_data/just_harris_high_quality.csv")
 saveRDS(linear_model, "models/linear_model.rds")
 

### 2024-11-04 paper/paper.qmd
Updated Paper

@@
 library(tidyverse)
+library(usmap)
+library(dplyr)
+library(here)
+library(ggplot2)
+library(janitor)
+library(knitr)
+library(flextable)
 ```
@@
 
-This analysis employs two predictive models to estimate the anticipated support for the two major candidates in the 2024 U.S.
+This analysis employs predictive models to estimate the anticipated support for the two major candidates in the 2024 U.S.
 Presidential Election: a multiple linear regression model.
@@
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+Predictors Selection: Variables such as sample_size, pollster, and state are included to capture systematic differences in polling methods and geographic variations in support.
+The date (end_date) of each poll controls for temporal effects on candidate popularity.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+Linear regression was chosen for this analysis due to several key advantages.
+First, its simplicity and interpret ability make it highly suitable for examining the relationship between predictor variables and the response variable, specifically the candidate support percentage.
+Each coefficient in a linear regression model clearly represents the influence of a predictor on the outcome, which facilitates straightforward interpretation and communication of results.
+Moreover, linear regression is computationally efficient, making it ideal for rapid model estimation, tuning, and testing, even on relatively large datasets.
 
-# Results
+## Regression Assumptions 
+- Linearity: The relationship between each predictor and the response (pct) is assumed to be linear.
+- Normality: Errors are assumed to follow a normal distribution, which is tested during model diagnostics.
 
-Our results are summarized in @tbl-modelresults.
+### Checking Assumptions
+
+```{r}
+#| tbl-cap: Checking Assumptions
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+linear_model <- readRDS(here::here("models/linear_model.rds"))
+
+plot(linear_model$fitted.values, residuals(linear_model), 
+     main = "Residuals vs Fitted", 
+     xlab = "Fitted values", 
+     ylab = "Residuals")
+
+# Q-Q Plot for Normality
+qqnorm(residuals(linear_model))
+qqline(residuals(linear_model))
+
+```
+In the Residuals vs.
+Fitted, there is no clear curved pattern, which suggests that the linear relationship might be appropriate.
+However, there are some clusters and a slight spread, which may indicate minor issues in capturing the relationship fully.
+Secondly, in the qqnorm plot, the points closely follow the diagonal line, indicating that residuals are approximately normal.
+This supports the normality assumption of the residuals, which is essential for reliable inference in linear regression.
+
+## Results
 
@@
 
-# Additional data details
+# Pollster Analysis
 
-# Model details {#sec-model-details}
+The Marquette Law School Poll employs a rigorous methodology to survey adults in the US on national issues, incorporating probability-based sampling that combines Address-Based Sampling (ABS) and Stratified Random Sampling [@citemarquette].
+This approach, including online and offline respondents, ensures broad representativeness.
+The SSRS Polling Panel supports participant recruitment, and weighting adjustments enhance result accuracy.
+
+## What is the population, frame, and sample?
+
+The population for the poll includes adults aged 18 and over across all 50 states and the District of Columbia.
+The sampling frame was constructed through ABS, leveraging the US Postal Service's Computerized Delivery Sequence (CDS), a comprehensive, regularly updated list of residential addresses.
+The primary source for participants is the SSRS Opinion Panel, which includes both ABS and telephone survey data to capture hard-to-reach demographics, like non-internet users.
+The survey ultimately included 1,005 adults, including registered and likely voters, with weighted samples to ensure proportional representation [@citemarquette].
+
+## How is the sample recruited?
+
+Participants were recruited via the SSRS Omnibus Panel, a probability panel formed from ABS and telephone survey data.
+This dual approach ensured that both internet and non-internet users were included, minimizing online-only bias.
+Stratified by demographics (age, gender, race, education, region, and partisan affiliation), this process produced a balanced representation across groups.
+Selected participants received an email invitation with a unique link to the survey.
+Non-responders received up to two reminder emails, and those who opted for text notifications also received reminders.
+Participants received an e-gift card incentive upon survey completion [@citemarquette].
+
+## What sampling approach is taken, and what are some of the trade-offs of this?
+
+The Marquette Law School Poll combines ABS and stratified random sampling.
+The ABS covers all residential addresses using USPS delivery sequences, ensuring broad geographic reach.
+To include hard-to-reach demographics, SSRS supplements ABS data with telephone survey responses.
+Stratified sampling by key demographics (age, gender, race, education, region, and political party) ensures representation across major groups [@citemarquette].
+This probability-based sampling minimizes bias but requires significant resources.
+Stratification and weighting to represent specific populations add to survey complexity and cost.
+
+## How is non-response handled?
+
+To address non-response and improve representativeness, SSRS applies weighting adjustments based on demographic variables such as age, gender, race, education, region, and internet use [@citemarquette].
+This process aligns sample characteristics with adult population parameters, reducing bias from demographic differences in response rates.
+
+## What is good and bad about the questionnaire?
+
+The questionnaire is well-designed, with a collaborative approach that reduces respondent burden and improves comprehension.
+A thoughtfully structured skip pattern enhances flow and minimizes dropout rates.
+The probability-based sampling, combined with extensive weighting and stratification, enables a representative sample of adults.
+However, heavy reliance on web-based responses may introduce internet bias, potentially underrepresenting non-internet households.
+Additionally, the questionnaire’s complexity may increase participant fatigue, affecting response completeness.
+The response rate of approximately 47.4% also indicates some level of attrition in the sample [@citemarquette].
 
@@
 
-# Pollster Analysis
-
-The Marquette Law School Poll employs a rigorous methodology to survey adults in the US on national issues, incorporating probability-based sampling that combines Address-Based Sampling (ABS) and Stratified Random Sampling [@citemarquette].
-This approach, including online and offline respondents, ensures broad representativeness.
-The SSRS Polling Panel supports participant recruitment, and weighting adjustments enhance result accuracy.
-
-## What is the population, frame, and sample?
-
-The population for the poll includes adults aged 18 and over across all 50 states and the District of Columbia.
-The sampling frame was constructed through ABS, leveraging the US Postal Service's Computerized Delivery Sequence (CDS), a comprehensive, regularly updated list of residential addresses.
-The primary source for participants is the SSRS Opinion Panel, which includes both ABS and telephone survey data to capture hard-to-reach demographics, like non-internet users.
-The survey ultimately included 1,005 adults, including registered and likely voters, with weighted samples to ensure proportional representation [@citemarquette].
-
-## How is the sample recruited?
-
-Participants were recruited via the SSRS Omnibus Panel, a probability panel formed from ABS and telephone survey data.
-This dual approach ensured that both internet and non-internet users were included, minimizing online-only bias.
-Stratified by demographics (age, gender, race, education, region, and partisan affiliation), this process produced a balanced representation across groups.
-Selected participants received an email invitation with a unique link to the survey.
-Non-responders received up to two reminder emails, and those who opted for text notifications also received reminders.
-Participants received an e-gift card incentive upon survey completion [@citemarquette].
-
-## What sampling approach is taken, and what are some of the trade-offs of this?
-
-The Marquette Law School Poll combines ABS and stratified random sampling.
-The ABS covers all residential addresses using USPS delivery sequences, ensuring broad geographic reach.
-To include hard-to-reach demographics, SSRS supplements ABS data with telephone survey responses.
-Stratified sampling by key demographics (age, gender, race, education, region, and political party) ensures representation across major groups [@citemarquette].
-This probability-based sampling minimizes bias but requires significant resources.
-Stratification and weighting to represent specific populations add to survey complexity and cost.
-
-## How is non-response handled?
-
-To address non-response and improve representativeness, SSRS applies weighting adjustments based on demographic variables such as age, gender, race, education, region, and internet use [@citemarquette].
-This process aligns sample characteristics with adult population parameters, reducing bias from demographic differences in response rates.
-
-## What is good and bad about the questionnaire?
-
-The questionnaire is well-designed, with a collaborative approach that reduces respondent burden and improves comprehension.
-A thoughtfully structured skip pattern enhances flow and minimizes dropout rates.
-The probability-based sampling, combined with extensive weighting and stratification, enables a representative sample of adults.
-However, heavy reliance on web-based responses may introduce internet bias, potentially underrepresenting non-internet households.
-Additionally, the questionnaire’s complexity may increase participant fatigue, affecting response completeness.
-The response rate of approximately 47.4% also indicates some level of attrition in the sample [@citemarquette].
-
 \newpage

### 2024-11-04 paper/paper.qmd
Updated Question Mark
Updated Scripts

@@
 
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+all_states <- c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", "Connecticut", "Delaware", "Florida", "Georgia", "Hawaii", "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky", "Louisiana", "Maine", "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi", "Missouri", "Montana", "Nebraska", "Nevada", "New Hampshire", "New Jersey", "New Mexico", "New York", "North Carolina", "North Dakota", "Ohio", "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island", "South Carolina", "South Dakota", "Tennessee", "Texas", "Utah", "Vermont", "Virginia", "Washington", "West Virginia", "Wisconsin", "Wyoming")
+
+just_harris <- read.csv(here("data/02-analysis_data/just_harris.csv"))
+just_harris$end_date <- as.Date(just_harris$end_date)
+just_harris$predicted_pct <- predict(linear_model, newdata = just_harris)
+
+# Calculate the average pct for each state
+state_avg_pct <- just_harris %>%
+  group_by(state) %>%
+  summarize(avg_pct = mean(pct, na.rm = TRUE))
+
+# Classify each state as a "win" or "loss" based on a 50% threshold and handle NA values
+state_avg_pct <- state_avg_pct %>%
+  mutate(win_state = ifelse(avg_pct > 50, "Harris Win", "Harris Loss"))
+
+# Replace NA values with "Uncertain"
+state_avg_pct$win_state[is.na(state_avg_pct$win_state)] <- "Uncertain"
+
+# Convert win_state to a factor to control levels and ensure "Uncertain" is displayed in the legend
+state_avg_pct$win_state <- factor(state_avg_pct$win_state, levels = c("Harris Win", "Harris Loss", "Uncertain"))
+existing_states <- unique(state_avg_pct$state)
+missing_states <- setdiff(all_states, existing_states)
+missing_states_df <- data.frame(
+  state = missing_states,
+  avg_pct = NA,  # No average percentage available
+  win_state = "Uncertain"
+)
+state_avg_pct_complete <- bind_rows(state_avg_pct, missing_states_df)
+state_avg_pct_complete <- state_avg_pct_complete %>% arrange(state)
+
+state_avg_pct_complete$win_state <- factor(state_avg_pct_complete$win_state, 
+                                           levels = c("Harris Win", "Harris Loss", "Uncertain"))
+
+# Plot the map with the updated classifications
+plot_usmap(data = state_avg_pct_complete, values = "win_state", regions = "states") +
+  scale_fill_manual(values = c("Harris Win" = "blue", "Harris Loss" = "red", "Uncertain" = "gray"), 
+                    name = "Prediction Outcome") +
+  labs(title = "Predicted 2024 Presidential Election Outcome for Kamala Harris",
+       subtitle = "States where Kamala Harris is predicted to win (blue) or lose (red), unpolled states as Uncertain (gray)") +
+  theme_minimal()
+
+```
+
 # Discussion
@@
 The proposed survey is designed using Google Forms,
-https://docs.google.com/forms/d/e/1FAIpQLSeHHeKaryNQ6sKgbuOH-ZgXwQYkNw9jBdxIbgeXWVj_t1ob2w/viewform?usp=sf_link
+https://forms.gle/Vhmm1b1XnqTSoBWq8
 
@@
 
-7. **In which U.S. state do you currently reside**
-  - ______________
+7. **In which U.S. state do you currently reside?**
+  - ___
 

### 2024-11-04 paper/paper.qmd
Updated Paper

--- 2024-11-04 paper/paper.qmd
@@
 date-format: long
-abstract: "This paper presents a multiple linear regression model and a bayesian model for forecasting the outcome of the 2024 U.S.
-Presidential Election.
-Using the data collected from high-quality polls from various pollsters, we generate these models by selecting relevant variables such as sample size, percentage support for each candidate, and sate.
-By comparing the predictive power of both models, we aim to provide a reliable forecast of the election outcome and a deeper understanding of public sentiment and polling reliability."
+abstract: ""
 format: pdf
@@
 
-Add graphs, tables and text.
+To accurately predict the 2024 Presidential Election, we have identified several key variables that capture a range of factors influencing voter behavior. These predictor variables include:
 
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
+- Polling Percentage (PCT): Represents the percentage of respondents in a poll who support a specific candidate
+- Numeric Grade (numeric_grade): Represents the rating of the pollster to indicate their quality
+- Sample Size (sample_size): size of the respondents participating in the poll
+- State (state): the state of the poll was taken in 
+- End_date: the day the poll ended
+- Start_date: the day the poll started
 
@@
 \begin{align*}
-\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{sample\_size}_i + \beta_3 \cdot \text{transparency\_score}_i \\
-&\quad + \sum_{k=1}^{K} \delta_k \cdot \text{state}_{ik} + \beta_4 \cdot \text{end\_date}_i + \epsilon_i,
+\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{sample\_size}_i + \sum_{k=1}^{K} \delta_k \cdot \text{state}_{ik} + \beta_4 \cdot \text{end\_date}_i + \epsilon_i,
 \end{align*}
@@
 - sample_size: The total number of respondents participating in the poll (e.g., 2712).
-- transparency_score:A score reflecting the pollster’s transparency about their methodology (e.g., 9.0).
-"A grade for how transparent a pollster is, calculated based on how much information it discloses about its polls and weighted by recency.
-The highest Transparency Score is 10."
 - state: The U.S. state where the poll was conducted or focused, if applicable.
@@
 
-```{r}
-#| tbl-cap: Checking Assumptions
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-linear_model <- readRDS(here::here("models/linear_model.rds"))
-
-plot(linear_model$fitted.values, residuals(linear_model), 
-     main = "Residuals vs Fitted", 
-     xlab = "Fitted values", 
-     ylab = "Residuals")
-
-# Q-Q Plot for Normality
-qqnorm(residuals(linear_model))
-qqline(residuals(linear_model))
-
-```
 In the Residuals vs.
@@
 The proposed survey is designed using Google Forms,
-https://docs.google.com/forms/d/e/1FAIpQLSeHHeKaryNQ6sKgbuOH-ZgXwQYkNw9jBdxIbgeXWVj_t1ob2w/viewform?usp=sf_link
+https://forms.gle/Vhmm1b1XnqTSoBWq8
 
 ## Survey Copy 
+Welcome to our survey!
+We are conducting research to understand public perceptions and opinions related to the upcoming 2024 Presidential Election.
+Your responses are valuable in helping us gain insight into voter perspectives and preferences.
+
+Contact Information: For any questions regarding this survey, please contact:
+
+Name: [Jason Yang]
+Email: ["jzc.yang@mail.utoronto.ca"]
+Phone: ["123-234-5678"]
+
+Your responses are confidential and will be used only for research purposes. This survey will take approximately [estimated time] to complete.
 
@@
 
+Thank you for taking the time to complete our survey. Your input is greatly appreciated and will contribute to our understanding of public opinion for the upcoming 2024 Presidential Election.
+
 \newpage

### 2024-11-04 scripts/00-simulate_data.R
updated scripts for electoral college projection vision

@@ -2,7 +2,7 @@
 # Purpose: To simulate plausible polling data for Kamala Harris's performance in the 
 #          2024 U.S. presidential election.
 # Authors: Peter Fan, Jerry Xia, Jason Yang
-# Date: 01 November 2024
+# Date: 04 November 2024
 # Contact: 
 # License: None
 # Pre-requisites:
@@ -14,11 +14,12 @@ library(tidyverse)
 library(here)
 set.seed(666)
 
-
 #### Simulate data ####
 states <- state.name
 n_polls <- 100  # Number of polls to simulate
 candidates <- c("Donald Trump", "Kamala Harris")
+
+# Extract unique pollsters from the existing analysis dataset
 pollsters <- Analysis_data %>% distinct(pollster) %>% pull(pollster)
 
 # Generate simulated data
@@ -27,16 +28,16 @@ simulated_data <- tibble(
   candidate = sample(candidates, n_polls, replace = TRUE),
   state = sample(states, n_polls, replace = TRUE),
   pollster = sample(pollsters, n_polls, replace = TRUE),
-  sample_size = sample(500:1000, n_polls, replace = TRUE),  # Random sample sizes between 500 and 3000
+  sample_size = sample(500:1000, n_polls, replace = TRUE),  # Random sample sizes between 500 and 1000
   pct = round(runif(n_polls, 40, 60), 1)  # Random polling percentage between 40% and 60%
 )
 
-# Adjust polling percentages to ensure that each candidate has plausible values
-stimulated_votes <- Analysis_data %>%
+# Adjust polling percentages to ensure each candidate has plausible values
+simulated_votes <- simulated_data %>%
   mutate(votes = round((pct / 100) * sample_size)) %>%  # Calculate number of votes per poll
-  group_by(candidate_name, state) %>%                   # Group by candidate and state
-  summarize(total_votes = sum(votes, na.rm = TRUE)) %>% # Sum votes within each group
-  ungroup()                                             # Remove grouping for a clean data frame
+  group_by(candidate, state) %>%                        # Group by candidate and state
+  summarize(total_votes = sum(votes, na.rm = TRUE)) %>%  # Sum votes within each group
+  ungroup()                                              # Remove grouping for a clean data frame
 
-write_csv(simulated_data, "data/00-simulated_data/simulated_data.csv")
-
+# Save simulated data
+write_csv(simulated_data, here("data/00-simulated_data/simulated_data.csv"))

### 2024-11-04 scripts/01-test_simulated_data.R

@@ -2,42 +2,33 @@
 # Purpose: To generate and validate simulated polling data for Donald Trump and Kamala Harris,
 #          including basic checks on data structure, ranges, and consistency of values.
 # Authors: Peter Fan, Jerry Xia, Jason Yang
-# Date: 01 November 2024
+# Date: 04 November 2024
 # License: None
 # Pre-requisites:
 # - Ensure that 'tidyverse' is installed for data manipulation.
-# - The 'Analysis_data' dataset should be loaded with valid pollster data.
-# - This script will output a CSV file of the simulated data in the "data/00-test_data" directory.
-# - Run this script after generating simulated data to validate its integrity and consistency.
+# - This script will validate the integrity and consistency of the simulated data.
 
 #### Workspace setup ####
 library(tidyverse)
 
+# Load the simulated data
 test_data <- read_csv("data/00-simulated_data/simulated_data.csv")
-
-# Test if the data was successfully loaded
-if (exists("analysis_data")) {
-  message("Test Passed: The dataset was successfully loaded.")
-} else {
-  stop("Test Failed: The dataset could not be loaded.")
-}
-
 
 #### Test data ####
 
-# Check if the dataset has 100 rows
+# Test if the dataset has 100 rows
 if (nrow(test_data) == 100) {
   message("Test Passed: The dataset has 100 rows.")
 } else {
   stop("Test Failed: The dataset does not have 100 rows.")
 }
 
-# Check if the dataset has all the columns
+# Check if the dataset has all the expected columns
 expected_columns <- c("poll_id", "candidate", "state", "pollster", "sample_size", "pct")
 if (all(expected_columns %in% colnames(test_data))) {
-  message("Test Passed: The dataset has all the columns.")
+  message("Test Passed: The dataset has all the expected columns.")
 } else {
-  stop("Test Failed: The dataset does not have 3 columns.")
+  stop("Test Failed: The dataset does not have all the expected columns.")
 }
 
 # Test if data types are correct
@@ -52,31 +43,30 @@ if (is.numeric(test_data$poll_id) &&
   stop("Test Failed: One or more columns in 'test_data' have incorrect data types.")
 }
 
-# Test if candidate only contains "Donald Trump" and "Kamala Harris"
+# Test if 'candidate' only contains "Donald Trump" and "Kamala Harris"
[…]

### 2024-11-04 paper/paper.qmd
Finished Survey

@@
 The survey itself will be concise and straightforward, focusing on voting intentions, key issues, and demographic information.
-For data validation, in the survey, we will include attention-check questions as respondents are very likely to complete the form for an entry into a prize draw.
+For data validation, the survey will include attention-check questions as respondents are very likely to complete the form for an entry into a prize draw.
 We will also conduct multiple waves of the survey, we will adopt a "poll-of-polls" approach, aggregating responses from different waves while applying weights based on relevance.
@@
 We will ensure that participants’ responses remain anonymous and that all data is handled securely.
-Transparency is also essential; respondents will be informed about the survey’s sponsorship, methodology, and data use
+Transparency is also essential; respondents will be informed about the survey’s sponsorship, methodology, and data use.
 
 The survey will be implemented on Google Forms, with a link provided in the appendix. We also included the questions in the appendix for better understandings.
+
+### Budget Allocation
+
+-
 
@@
 Your responses are valuable in helping us gain insight into voter perspectives and preferences.
+By participating, you will gain the chance to enter a prize draw. Prizes include a chance to win gift cards, exclusive merchandise, and special deals with our sponsors.
 
-Contact Information: For any questions regarding this survey, please contact:
+The survey should take about 10-15 minutes to complete.
 
-Name: [Jason Yang]
-Email: ["jzc.yang@mail.utoronto.ca"]
-Phone: ["123-234-5678"]
+Please note:
 
-Your responses are confidential and will be used only for research purposes. This survey will take approximately [estimated time] to complete.
+- Your Privacy are our top concern. All responses are confidential and will be used solely for research purposes. 
+- Participation is entirely voluntary.
 
-1. **Who do you intend to vote for in the 2024 U.S. Presidential Election?**
+Contact Information
+
+If you have any inquiries or need assistance with this survye, please contact us at:
+
+- jzc.yang@mail.utoronto.ca
+- 123-456-7891
+
+1. **Are you eligible to vote in the upcoming 2024 U.S. Presidential Election?**
+  - Yes 
+  - No 
+  - Not sure
+
+2. **Who do you intend to vote for in the 2024 U.S. Presidential Election?**
   - Kamala Harris (Democratic Party)
@@
 
-2. **How certain are you about your choice?  **
+3. **How certain are you about your choice?  **
   - Very Certain
@@
 
-3. **Which of the following issues are most important in deciding your vote? (Select up to 3)**
+4. **Which of the following issues are most important in deciding your vote? (Select up to 3)**
   - Economy and jobs
@@
 
-4. **What is your age?**
+5. **What is your age?**
   - 18-24
@@
 
-5. **What is your gender?**
+6. **What is your gender?**
   - Male 
   - Female
-  - Non-binary/Other
+  - Non-binary
   - Prefer not to say
+  - Other:
 
-6. **What is your race/ethnicity? (Select all that apply)**
+7. **What is your race/ethnicity? (Select all that apply)**
   - White
@@
 
-7. **In which U.S. state do you currently reside?**
-  - ___
+8. **In which U.S. state do you currently reside?**
+  - [Drop Down With All the States]
 
-8. **If you voted in 2020, who did you vote for?**
+9. **If you voted in 2020, who did you vote for?**
   - Joe Biden 
@@
   - Other:
+
+10. **Source of Information: What are your primary sources for political news?**
+  - Television
+  - Newspapers/Magazines
+  - Online News Websites
+  - Social Media
+  - Radio 
+  - Friends and Family 
+  - Other (Please specify): _____
+
+11. **What is your highest level of education?**
+  - High school graduate, equivalent, or less
+  - College Degree
+  - Associate degree
+  - Bachelor's degree
+  - Graduate degree
+
+12. **Would you be willing to participate in follow-up surveys regarding the election?** 
+  - Yes
+  - No
+
+13. **Do you have any additional comments or concerns about the 2024 election?**
+  - [Open Text Response]
 

### 2024-11-04 paper/paper.qmd
Updated Paper
Fixed Typo

@@
 
-## Idealized Methodology
+# Idealized Methodology
 
@@
 
-### Budget Allocation
+## Budget Allocation
 
--
+- Sampling and Data Collection (Advertisements and Recruitment Platforms): $40,000
+- Participant Incentives (Prize Pool): $20,000
+- Survey Design and Testing: $20,000
+- Data Analysis and Validation: $20,000
 
-## Idealized Survey
+# Idealized Survey
 
@@
 
-If you have any inquiries or need assistance with this survye, please contact us at:
+If you have any inquiries or need assistance with this survey, please contact us at:
 

### 2024-11-04 scripts/00-simulate_data.R
updated simulate variables of interest

@@ -1,6 +1,6 @@
 #### Preamble ####
-# Purpose: To simulate plausible polling data for Kamala Harris's performance in the 
-#          2024 U.S. presidential election.
+# Purpose: To simulate polling data for Kamala Harris and Donald Trump in the 
+#          2024 U.S. presidential election, supporting a poll of polls approach.
 # Authors: Peter Fan, Jerry Xia, Jason Yang
 # Date: 04 November 2024
 # Contact: 
@@ -12,32 +12,26 @@
 #### Workspace setup ####
 library(tidyverse)
 library(here)
-set.seed(666)
+set.seed(304)
 
 #### Simulate data ####
+# Define parameters based on real data structure, keeping only relevant variables
 states <- state.name
 n_polls <- 100  # Number of polls to simulate
 candidates <- c("Donald Trump", "Kamala Harris")
+pollsters <- c("YouGov", "Ipsos", "CNN", "Gallup", "Emerson")  # Realistic pollster names
 
-# Extract unique pollsters from the existing analysis dataset
-pollsters <- Analysis_data %>% distinct(pollster) %>% pull(pollster)
-
-# Generate simulated data
+# Generate simulated data relevant for the poll-of-polls approach
 simulated_data <- tibble(
   poll_id = 1:n_polls,
   candidate = sample(candidates, n_polls, replace = TRUE),
   state = sample(states, n_polls, replace = TRUE),
   pollster = sample(pollsters, n_polls, replace = TRUE),
-  sample_size = sample(500:1000, n_polls, replace = TRUE),  # Random sample sizes between 500 and 1000
-  pct = round(runif(n_polls, 40, 60), 1)  # Random polling percentage between 40% and 60%
+  sample_size = sample(500:3000, n_polls, replace = TRUE),  # Sample sizes between 500 and 3000
+  pct = round(runif(n_polls, 40, 60), 1),  # Polling percentage between 40% and 60%
+  start_date = sample(seq(as.Date("2024-01-01"), as.Date("2024-10-01"), by = "day"), n_polls, replace = TRUE),
+  end_date = sample(seq(as.Date("2024-01-02"), as.Date("2024-10-02"), by = "day"), n_polls, replace = TRUE)
 )
 
-# Adjust polling percentages to ensure each candidate has plausible values
-simulated_votes <- simulated_data %>%
-  mutate(votes = round((pct / 100) * sample_size)) %>%  # Calculate number of votes per poll
[…]

### 2024-11-04 scripts/02-download_data.R

@@ -1,18 +1,17 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from 
-# Author: Group 15
-# Date: 11 February 2023 
-# Contact: rohan.alexander@utoronto.ca 
-# License: MIT
+# Purpose: To load polling data from FiveThirtyEight for the 2024 U.S. presidential election.
+# Authors: Peter Fan, Jerry Xia, Jason Yang
+# Date: 04 November 2024
+# Contact: 
+# License: None
 # Pre-requisites: 
-# Any other information needed? 
-
+# - Ensure that the 'tidyverse' and 'here' packages are installed for data manipulation.
+# - The raw data ('president_polls.csv') should be manually added to the project folder.
 
 #### Workspace setup ####
-library(opendatatoronto)
 library(tidyverse)
+library(here)
 
-#### Save data ####
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
-
-         
+#### Load data ####
+# Load the manually provided raw data
+the_raw_data <- read_csv(here("data/president_polls.csv"))

### 2024-11-04 scripts/00-simulate_data.R
cleaned up uneeded files in folder and reorganized model location

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: To simulate polling data for Kamala Harris and Donald Trump in the 
+# Purpose: To simulate plausible polling data for Kamala Harris and Donald Trump in the 
 #          2024 U.S. presidential election, supporting a poll of polls approach.
 # Authors: Peter Fan, Jerry Xia, Jason Yang
 # Date: 04 November 2024
@@ -23,7 +23,6 @@ pollsters <- c("YouGov", "Ipsos", "CNN", "Gallup", "Emerson")  # Realistic polls
 
 # Generate simulated data relevant for the poll-of-polls approach
 simulated_data <- tibble(
-  poll_id = 1:n_polls,
   candidate = sample(candidates, n_polls, replace = TRUE),
   state = sample(states, n_polls, replace = TRUE),
   pollster = sample(pollsters, n_polls, replace = TRUE),

### 2024-11-04 scripts/02-download_data.R

@@ -14,4 +14,4 @@ library(here)
 
 #### Load data ####
 # Load the manually provided raw data
-the_raw_data <- read_csv(here("data/president_polls.csv"))
+the_raw_data <- read_csv(here("data/01-raw_data/president_polls.csv"))

### 2024-11-04 scripts/03-clean_data.R

@@ -2,50 +2,42 @@
 # Purpose: To read and clean data on 2024 U.S. presidential election polling 
 #          from the FiveThirtyEight poll aggregation at 
 #          https://projects.fivethirtyeight.com/polls/president-general/2024/national/.
-# Author: Peter Fan, Jerry Xia, Jason Yang
-# Date: 01 November 2024
+# Authors: Peter Fan, Jerry Xia, Jason Yang
+# Date: 04 November 2024
 # Contact: 
 # License: None
+# Pre-requisites: 
 # - Ensure the 'tidyverse' and 'janitor' packages are installed for data manipulation.
 # - Data should be downloaded and saved in the local project directory in a 'data/01-raw_data' folder.
 
 #### Workspace setup ####
 library(tidyverse)
+library(janitor)
+library(lubridate)
 
 #### Clean data ####
 
+# Load raw data
 raw_data <- read_csv("data/01-raw_data/president_polls.csv") |>
   clean_names()
 
-Analysis_data <- raw_data  %>% 
-  select(candidate_name, pollster, sample_size, end_date, numeric_grade, methodology, state, pct, pollscore, transparency_score, start_date) %>%
-  mutate(
-    end_date = mdy(end_date),
-    start_date = mdy(start_date)
-  ) %>%
+# Select and clean relevant columns
+analysis_data <- raw_data %>% 
+  select(candidate_name, pollster, sample_size, end_date, state, pct) %>%
+  mutate(end_date = mdy(end_date)) %>%
   filter(candidate_name %in% c("Donald Trump", "Kamala Harris"))
 
-Analysis_data <- Analysis_data %>%
+# Adjust state names for Nebraska and Maine districts
+analysis_data <- analysis_data %>%
   mutate(state = case_when(
     state == "Nebraska CD-2" ~ "Nebraska",
-    state == "Maine CD-1" ~ "Maine" , 
+    state == "Maine CD-1" ~ "Maine", 
     state == "Maine CD-2" ~ "Maine",
     TRUE ~ state  # Keeps all other values as they are
   ))
 
-Analysis_data <- Analysis_data %>% drop_na()
+# Drop rows with missing values
+analysis_data <- analysis_data %>% drop_na()
 
-Analysis_data <- Analysis_data %>% filter(numeric_grade >= 1)
-
-just_harris_high_quality <- Analysis_data |>
-  filter(
-    candidate_name == "Kamala Harris",
[…]

### 2024-11-04 scripts/04-test_analysis_data.R

@@ -1,30 +1,29 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
+# Purpose: To test the integrity and structure of the cleaned data from the 2024 U.S. presidential election polling.
+# Authors: Peter Fan, Jerry Xia, Jason Yang
+# Date: 04 November 2024
+# Contact: 
+# License: None
+# Pre-requisites: 
+# - Ensure the 'tidyverse' and 'testthat' packages are installed for data manipulation and testing.
+# - The cleaned data must be available in 'data/02-analysis_data/analysis_data.csv'.
 
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)
 
+# Load the cleaned data
 analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
-
 
 #### Test data ####
 
 # Test 1: Check that the dataset has the expected columns
 test_that("dataset has required columns", {
-  required_columns <- c("candidate_name", "pollster", "sample_size", "end_date", 
-                        "numeric_grade", "methodology", "state", "pct", "pollscore")
+  required_columns <- c("candidate_name", "pollster", "sample_size", "end_date", "state", "pct")
   expect_true(all(required_columns %in% colnames(analysis_data)))
 })
 
-# Test 3: Validate data types for key columns
+# Test 2: Validate data types for key columns
 test_that("data types are correct for key columns", {
   expect_type(analysis_data$candidate_name, "character")
   expect_type(analysis_data$pollster, "character")
@@ -32,19 +31,19 @@ test_that("data types are correct for key columns", {
   expect_type(analysis_data$pct, "double")
 })
 
-# Test 4: Check `pct` is within valid range (0 to 100)
+# Test 3: Check `pct` is within valid range (0 to 100)
 test_that("'pct' values are within the valid range (0 to 100)", {
   expect_true(all(analysis_data$pct >= 0 & analysis_data$pct <= 100))
 })
 
-# Test 5: Check that `numeric_grade` is within expected range (1.0 to 5.0)
-test_that("'numeric_grade' is within the expected range", {
[…]

### 2024-11-04 scripts/05-exploratory_data_analysis.R

@@ -1,37 +1,29 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
+# Purpose: To model the 2024 U.S. presidential election polling data to predict support for candidates.
+# Authors: Peter Fan, Jerry Xia, Jason Yang
+# Date: 04 November 2024
+# Contact: 
+# License: None
+# Pre-requisites: 
+# - Ensure the 'tidyverse' package is installed for data manipulation and modeling.
+# - The cleaned data must be available in 'data/02-analysis_data/analysis_data.csv'.
 
 #### Workspace setup ####
 library(tidyverse)
-library(rstanarm)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
 
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
+#### Model data ####
+# Fit a model to predict support for the candidates using polling data
+support_model <-
+  lm(
+    formula = pct ~ candidate_name + state + sample_size + pollster,
+    data = analysis_data
   )
-
 
 #### Save model ####
 saveRDS(
-  first_model,
-  file = "models/first_model.rds"
+  support_model,
+  file = "models/support_model.rds"
 )
-
-

### 2024-11-04 scripts/06-pollster_analysis.R
fixed some file name inconsistencies within scripts and updated pollster analysis

@@ -1,0 +1,49 @@
+#### Preamble ####
+# Purpose: To analyze the pollsters used in the 2024 U.S. presidential election polling data, evaluating credibility and identifying patterns or biases.
+# Authors: Peter Fan, Jerry Xia, Jason Yang
+# Date: 04 November 2024
+# Contact: 
+# License: None
+# Pre-requisites: 
+# - Ensure the 'tidyverse' package is installed for data manipulation.
+# - The cleaned data must be available in 'data/02-analysis_data/analysis_data.csv'.
+
+#### Workspace setup ####
+library(tidyverse)
+
+#### Read data ####
+analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
+
+#### Pollster Analysis ####
+# Summary statistics by pollster
+df_pollster_summary <- analysis_data %>%
+  group_by(pollster) %>%
+  summarise(
+    avg_support = mean(pct, na.rm = TRUE),
+    sd_support = sd(pct, na.rm = TRUE),
+    total_polls = n(),
+    avg_sample_size = mean(sample_size, na.rm = TRUE)
+  ) %>%
+  arrange(desc(total_polls))
+
+# Get the top 10 pollsters by number of polls
+top_10_pollsters <- df_pollster_summary %>%
+  top_n(10, total_polls)
+
+# Plot average support by the top 10 pollsters
+plot_pollster_support_top_10 <- top_10_pollsters %>%
+  ggplot(aes(x = reorder(pollster, -avg_support), y = avg_support)) +
+  geom_col(fill = "skyblue") +
+  coord_flip() +
+  labs(
+    title = "Average Candidate Support by Top 10 Pollsters",
+    x = "Pollster",
+    y = "Average Support (%)"
+  ) +
+  theme_minimal()
+
+# Save the updated plot
+ggsave("figures/pollster_support_analysis_top_10.png", plot_pollster_support_top_10, width = 10, height = 8)
+
+# Save summary statistics
+write_csv(df_pollster_summary, "data/03-analysis_summary/pollster_summary.csv")

### 2024-11-04 scripts/07-electoral_college_projection.R
updated electoral college projection and uncertainty propagation

@@ -1,0 +1,75 @@
+#### Preamble ####
+# Purpose: To estimate the electoral college outcome for the 2024 U.S. presidential election using polling data, propagating uncertainty.
+# Authors: Peter Fan, Jerry Xia, Jason Yang
+# Date: 04 November 2024
+# Contact: 
+# License: None
+# Pre-requisites: 
+# - Ensure the 'tidyverse' package is installed for data manipulation.
+# - The cleaned data must be available in 'data/02-analysis_data/analysis_data.csv'.
+
+#### Workspace setup ####
+library(tidyverse)
+
+#### Create necessary directories ####
+if (!dir.exists("data/04-electoral_college_estimate")) {
+  dir.create("data/04-electoral_college_estimate", recursive = TRUE)
+}
+
+#### Read data ####
+analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
+
+#### Electoral College Estimate with Uncertainty ####
+# Assign electoral votes to each state
+# Updated electoral vote data
+electoral_votes <- tibble(
+  state = c(state.name, "District of Columbia"),
+  electoral_votes = c(9, 3, 11, 6, 54, 10, 7, 3, 30, 16, 4, 4, 19, 11, 6, 6, 8, 10, 4, 10, 11, 16, 10, 11, 3, 4, 14, 5, 6, 28, 16, 3, 17, 7, 8, 19, 4, 9, 3, 11, 40, 6, 3, 13, 12, 4, 9, 3, 11, 10, 3)
+)
+
+# Calculate average polling support and standard deviation by state for each candidate
+state_support_stats <- analysis_data %>%
+  group_by(state, candidate_name) %>%
+  summarise(
+    avg_support = mean(pct, na.rm = TRUE),
+    sd_support = sd(pct, na.rm = TRUE)
+  ) %>%
+  ungroup()
+
+# Join electoral votes data
+state_support_stats <- state_support_stats %>%
+  left_join(electoral_votes, by = "state")
+
+# Set number of simulations
+n_simulations <- 1000
+
+# Run Monte Carlo simulations for electoral college estimate
+set.seed(853)
+sim_results <- replicate(n_simulations, {
+  # Simulate support for each candidate in each state
+  simulated_support <- state_support_stats %>%
+    mutate(simulated_pct = rnorm(n(), mean = avg_support, sd = sd_support)) %>%
+    group_by(state) %>%
[…]

### 2024-11-04 scripts/08-model_data.R

@@ -1,51 +1,45 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
+# Purpose: To analyze the results of the linear model for Kamala Harris's polling performance in the 2024 U.S. presidential election.
+# Authors: Peter Fan, Jerry Xia, Jason Yang
+# Date: 04 November 2024
+# Contact: 
+# License: None
+# Pre-requisites: 
+# - Ensure the necessary packages ('tidyverse', 'broom', 'modelsummary') are installed for data manipulation and model analysis.
+# - The linear model must be available in 'models/linear_model.rds'.
 
 #### Workspace setup ####
 library(tidyverse)
-library(janitor)
-library(lubridate)
 library(broom)
 library(modelsummary)
-library(rstanarm)
-library(splines)
-library(here)
 
-#### Read data ####
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
+#### Read model ####
+linear_model <- readRDS("models/linear_model.rds")
 
-just_harris_high_quality <- read.csv("data/02-analysis_data/just_harris_high_quality.csv")
+#### Model Analysis ####
+# Get a tidy summary of the linear model
+model_summary <- tidy(linear_model)
 
-just_harris_high_quality <- just_harris_high_quality %>%
-  mutate(
-    pollster = as.factor(pollster),
-    state = as.factor(state),
-    methodology = factor(methodology),
-    numeric_grade = as.numeric(numeric_grade),
-    transparency_score = as.numeric(transparency_score),
-    sample_size = as.numeric(sample_size),
-    end_date = as.Date(end_date),
-    start_date = as.Date(start_date)
-  )
+# Print model summary to console
+print(model_summary)
 
+# Save model summary as CSV
+write_csv(model_summary, "data/05-model_results/linear_model_summary.csv")
 
-linear_model <- lm(
-  pct ~ pollscore + numeric_grade + sample_size + state + end_date, 
-  data = just_harris_high_quality
-)
+# Create a visual summary of the model coefficients
[…]

### 2024-11-04 paper/paper.qmd
Survey Updated

--- 2024-11-04 paper/paper.qmd
@@
   - Jason Yang
-  - Another author
+  - Jerry Xia 
+  - Peter Fan
 thanks: "Code and data are available at: [https://github.com/Jerryx2020/US_election_prediction/tree/main]."
@@
 format: pdf
+header-includes: 
+  - \usepackage{pdfpages}
 number-sections: true
@@
 - Polling Percentage (PCT): Represents the percentage of respondents in a poll who support a specific candidate
-- Numeric Grade (numeric_grade): Represents the rating of the pollster to indicate their quality
+- Pollster: Represents the name of the polling organization that conducted the poll. 
+- Candidate: The name of the candidate in the poll
 - Sample Size (sample_size): size of the respondents participating in the poll
@@
 \begin{align*}
-\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{numeric\_grade}_i + \beta_2 \cdot \text{sample\_size}_i + \sum_{k=1}^{K} \delta_k \cdot \text{state}_{ik} + \beta_4 \cdot \text{end\_date}_i + \epsilon_i,
+\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{pollster}_i + \beta_2 \cdot \text{sample\_size}_i + \sum_{k=1}^{K} \delta_k \cdot \text{state}_{ik} + \beta_4 \cdot \text{end\_date}_i + \beta_5 \cdot \text{candidate}_i + \epsilon_i,
 \end{align*}
 
-- pct: The percentage of the vote or support that the candidate received in the poll (e.g., 51.0 for Kamala Harris, 48.0 for Donald Trump).
-- numeric_grade: A numeric rating given to the pollster to indicate their quality or reliability (e.g., 3.0).
-- sample_size: The total number of respondents participating in the poll (e.g., 2712).
-- state: The U.S. state where the poll was conducted or focused, if applicable.
-- end_date: The date the poll ended (e.g., 10/11/24).
-- $\epsilon_i$: The error term for poll accounting for variability not explained by the predictors.
+Where
+
+- $\beta_0$ is the expected value of PCT when all predictor variables are zero, intercept 
+- $\beta_1$ captures the effect pollsters have on the response variable 
+- $\beta_2$ captures the effect sample_size have on the response variable
+- $\delta_k$ captures the difference in PCT between states
+- $\beta_4$ captures the expected change in PCT for each additional unit increase in the end date variable 
+- $\beta_5$ captures the difference in PCT associated with difference candidates
 
@@
 # Discussion
-
-## First discussion point {#sec-first-point}
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
-
-## Second discussion point
-
-Please don't use these as sub-heading labels - change them to be what your point actually is.
-
-## Third discussion point
-
-## Weaknesses and next steps
-
-Weaknesses and next steps should also be included.
 
@@
 
-Our target population is voters aged 18 and above, with a sample size of approximately 10,000 responses, 200 responses from each state, to ensure a statistically significance at the national level and within key demographic groups.
+Our target population is voters aged 18 and above, with a sample size of approximately 10,000 responses, 200 responses from each state, to ensure  statistical significance at the national level and within key demographic groups.
 To achieve balanced representation, we will employ stratified random sampling based on age, gender, race/ethnicity, education, region, and urban/rural status.
@@
 
-For recruitment, we will combine online survey panels, social media outreach, and targeted telephone recruitment.
+We will combine online survey panels, social media outreach, and targeted telephone recruitment.
 These methods are chosen to increase accessibility for harder-to-reach demographics, such as older adults and rural residents.
@@
 
+To ensure data validity, IP addresses would be recorded to prevent multiple submissions from the same source.
+Additionally, cookies would be implemented to prevent users from retaking the survey on the same device.
+Finally, we will verify respondents' email addresses to ensure uniqueness.
+
 Ethically, our approach prioritizes respondent privacy and data security.
 We will ensure that participants’ responses remain anonymous and that all data is handled securely.
-Transparency is also essential; respondents will be informed about the survey’s sponsorship, methodology, and data use
+Transparency is also essential; respondents will be informed about the survey’s sponsorship, methodology, and data use.
 
@@
 
-## Idealized Survey
+## Budget Allocation
+
+- Sampling and Data Collection (Advertisements and Recruitment Platforms): $40,000
+- Participant Incentives (Prize Pool): $20,000
+- Survey Design and Testing: $20,000
+- Data Analysis and Validation: $20,000
+
+# Idealized Survey
 
@@
 ## Survey Copy
-Welcome to our survey!
-We are conducting research to understand public perceptions and opinions related to the upcoming 2024 Presidential Election.
-Your responses are valuable in helping us gain insight into voter perspectives and preferences.
 
-Contact Information: For any questions regarding this survey, please contact:
-
-Name: [Jason Yang]
-Email: ["jzc.yang@mail.utoronto.ca"]
-Phone: ["123-234-5678"]
-
-Your responses are confidential and will be used only for research purposes. This survey will take approximately [estimated time] to complete.
-
-1. **Who do you intend to vote for in the 2024 U.S. Presidential Election?**
-  - Kamala Harris (Democratic Party)
-  - Donald Trump (Republican Party)
-  - Undecided 
-  - Other:
-
-2. **How certain are you about your choice?  **
-  - Very Certain
-  - Somewhat certain
-  - Unsure
-
-3. **Which of the following issues are most important in deciding your vote? (Select up to 3)**
-  - Economy and jobs
-  - Healthcare
-  - Climate Change
-  - Education
-  - Immigration
-  - National Security 
-  - Social justice and Equality 
-  - Abortion rights
-  - Gun control
-  - Other:
-
-4. **What is your age?**
-  - 18-24
-  - 24-34
-  - 35-44
-  - 45-54
-  - 55-64
-  - 65 or older
-
-5. **What is your gender?**
-  - Male 
-  - Female
-  - Non-binary/Other
-  - Prefer not to say
-
-6. **What is your race/ethnicity? (Select all that apply)**
-  - White
-  - Black or African American 
-  - Hispanic or Latino 
-  - Asian
-  - Native American or Alaska Native
-  - Native Hawaiian or Other Pacific Islander 
-  - Other:
-
-7. **In which U.S. state do you currently reside?**
-  - ___
-
-8. **If you voted in 2020, who did you vote for?**
-  - Joe Biden 
-  - Donald Trump 
-  - Other:
-
-Thank you for taking the time to complete our survey. Your input is greatly appreciated and will contribute to our understanding of public opinion for the upcoming 2024 Presidential Election.
+\includepdf[pages=-]{../other/Survey/Survey.pdf}
 

### 2024-11-04 scripts/03-clean_data.R
organized the model scripts to be in line with our data's narrative

@@ -15,29 +15,41 @@ library(tidyverse)
 library(janitor)
 library(lubridate)
 
-#### Clean data ####
-
-# Load raw data
+#### Read raw data ####
 raw_data <- read_csv("data/01-raw_data/president_polls.csv") |>
   clean_names()
 
-# Select and clean relevant columns
+#### Data Cleaning ####
+# Select and clean relevant columns for analysis
 analysis_data <- raw_data %>% 
   select(candidate_name, pollster, sample_size, end_date, state, pct) %>%
-  mutate(end_date = mdy(end_date)) %>%
-  filter(candidate_name %in% c("Donald Trump", "Kamala Harris"))
+  mutate(
+    end_date = mdy(end_date),
+    state = case_when(
+      state == "Nebraska CD-2" ~ "Nebraska",
+      state == "Maine CD-1" ~ "Maine", 
+      state == "Maine CD-2" ~ "Maine",
+      TRUE ~ state
+    )
+  ) %>%
+  filter(candidate_name %in% c("Donald Trump", "Kamala Harris")) %>%
+  drop_na()
 
-# Adjust state names for Nebraska and Maine districts
+# Filter observations to include only recent polling data (after Harris was declared)
+cutoff_date <- as.Date("2024-07-21")
 analysis_data <- analysis_data %>%
-  mutate(state = case_when(
-    state == "Nebraska CD-2" ~ "Nebraska",
-    state == "Maine CD-1" ~ "Maine", 
-    state == "Maine CD-2" ~ "Maine",
-    TRUE ~ state  # Keeps all other values as they are
-  ))
+  filter(end_date >= cutoff_date)
 
-# Drop rows with missing values
-analysis_data <- analysis_data %>% drop_na()
+# Calculate poll recency to enhance depth of analysis
+reference_date <- max(analysis_data$end_date, na.rm = TRUE)
+analysis_data <- analysis_data %>%
+  mutate(recency = as.numeric(reference_date - end_date))
 
-# Save cleaned dataset
+# Remove pollsters with fewer than 5 polls to ensure data reliability
+analysis_data <- analysis_data %>%
+  group_by(pollster) %>%
+  filter(n() >= 5) %>%
+  ungroup()
+
+#### Save cleaned dataset ####
 write_csv(analysis_data, "data/02-analysis_data/analysis_data.csv")

### 2024-11-04 scripts/08-model_data.R

@@ -1,20 +1,40 @@
 #### Preamble ####
-# Purpose: To analyze the results of the linear model for Kamala Harris's polling performance in the 2024 U.S. presidential election.
+# Purpose: To build and analyze a linear model for Kamala Harris's polling performance in the 2024 U.S. presidential election.
 # Authors: Peter Fan, Jerry Xia, Jason Yang
 # Date: 04 November 2024
 # Contact: 
 # License: None
 # Pre-requisites: 
 # - Ensure the necessary packages ('tidyverse', 'broom', 'modelsummary') are installed for data manipulation and model analysis.
-# - The linear model must be available in 'models/linear_model.rds'.
+# - The cleaned data must be available in 'data/02-analysis_data/analysis_data.csv'.
 
 #### Workspace setup ####
 library(tidyverse)
 library(broom)
 library(modelsummary)
 
-#### Read model ####
-linear_model <- readRDS("models/linear_model.rds")
+#### Read data ####
+# Load cleaned dataset for Kamala Harris's polling performance
+analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
+
+# Filter data for Kamala Harris
+just_harris_high_quality <- analysis_data %>%
+  filter(candidate_name == "Kamala Harris") %>%
+  mutate(
+    pollster = as.factor(pollster),
+    state = as.factor(state),
+    sample_size = as.numeric(sample_size),
+    end_date = as.Date(end_date)
+  )
+
+#### Build Linear Model ####
+linear_model <- lm(
+  pct ~ sample_size + state + end_date, 
+  data = just_harris_high_quality
+)
+
+#### Save Model ####
+saveRDS(linear_model, "models/linear_model.rds")
 
 #### Model Analysis ####
 # Get a tidy summary of the linear model

### 2024-11-04 scripts/10-example_script.R

@@ -1,230 +1,0 @@
-#### Set-up ####
-# Load libraries
-library(tidyverse)
-library(janitor)
-library(lubridate)
-library(broom)
-library(modelsummary)
-library(rstanarm)
-library(splines)
-library(here)
-
-
-#### Prepare dataset ####
-# Read in the data and clean variable names
-data <- read_csv("data/01-raw_data/president_polls.csv") |>
-  clean_names()
-
-# Filter data to Harris estimates based on high-quality polls after she declared
-just_harris_high_quality <- data |>
-  filter(
-    candidate_name == "Kamala Harris",
-    numeric_grade >= 2.7 # Need to investigate this choice - come back and fix. 
-    # Also need to look at whether the pollster has multiple polls or just one or two - filter out later
-  ) |>
-  mutate(
-    state = if_else(is.na(state), "National", state), # Hacky fix for national polls - come back and check
-    end_date = mdy(end_date)
-  ) |>
-  filter(end_date >= as.Date("2024-07-21")) |> # When Harris declared
-  mutate(
-    num_harris = round((pct / 100) * sample_size, 0) # Need number not percent for some models
-  )
-
-
-#### Plot data ####
-base_plot <- ggplot(just_harris_high_quality, aes(x = end_date, y = pct)) +
-  theme_classic() +
-  labs(y = "Harris percent", x = "Date")
-
-# Plots poll estimates and overall smoothing
-base_plot +
-  geom_point() +
-  geom_smooth()
-
-# Color by pollster
-# This gets messy - need to add a filter - see line 21
-base_plot +
-  geom_point(aes(color = pollster)) +
-  geom_smooth() +
-  theme(legend.position = "bottom")
-
-# Facet by pollster
-# Make the line 21 issue obvious
-# Also - is there duplication???? Need to go back and check
-base_plot +
-  geom_point() +
-  geom_smooth() +
-  facet_wrap(vars(pollster))
-
-# Color by pollscore
-base_plot +
-  geom_point(aes(color = factor(pollscore))) +
-  geom_smooth() +
-  theme(legend.position = "bottom")
-
-
-#### Starter models ####
-# Model 1: pct as a function of end_date
-model_date <- lm(pct ~ end_date, data = just_harris_high_quality)
-
-# Model 2: pct as a function of end_date and pollster
[…]

### 2024-11-04 paper/paper.qmd
Updated the Pollster Appendix
Updated the Pollster Appendix

@@
 
-The Marquette Law School Poll employs a rigorous methodology to survey adults in the US on national issues, incorporating probability-based sampling that combines Address-Based Sampling (ABS) and Stratified Random Sampling [@citemarquette].
-This approach, including online and offline respondents, ensures broad representativeness.
-The SSRS Polling Panel supports participant recruitment, and weighting adjustments enhance result accuracy.
+The Marquette Law School Poll utilizes a rigorous probability-based methodology to conduct a national question survey of adults across the United States.
+This method combines address-based sampling (ABS), which uses the U.S.
+Postal Service's Computerized Delivery Sequence (CDS), and stratified random sampling, which covers virtually all residential addresses and is able to reach the offline population, thereby reducing the bias associated with surveys conducted solely via the Internet [@citemarquette].
+The stratified random sampling method divides the population into subgroups (e.g., age, gender, education), to make sure that each subgroup is proportionately represented in the sample.
+This structure improves representativeness and accuracy, thereby supporting valid inferences about the total U.S.
+adult population.
 
@@
 
-The population for the poll includes adults aged 18 and over across all 50 states and the District of Columbia.
-The sampling frame was constructed through ABS, leveraging the US Postal Service's Computerized Delivery Sequence (CDS), a comprehensive, regularly updated list of residential addresses.
-The primary source for participants is the SSRS Opinion Panel, which includes both ABS and telephone survey data to capture hard-to-reach demographics, like non-internet users.
-The survey ultimately included 1,005 adults, including registered and likely voters, with weighted samples to ensure proportional representation [@citemarquette].
+The population surveyed by the Marquette Law School Poll includes all U.S.
+adults aged 18 and older, living in the 50 states and D.C.
+The sampling frame was developed using Address-Based Sampling (ABS) by using the U.S.
+Postal Service’s Computerized Delivery Sequence (CDS) file—a regularly updated, near-complete listing of all residential addresses in the U.S., excluding business addresses.
+This frame can cover almost every U.S.
+household, including non-internet and traditionally hard-to-reach areas [@citemarquette].
+
+The sample itself was drawn from the SSRS Opinion Panel, a probability-based panel that combines participants from ABS and a bilingual telephone survey conducted through the SSRS Omnibus.
+This dual recruitment strategy, which includes participants from both internet and non-internet households, improves demographic inclusivity.
+To achieve accurate representation, the survey sampled 1,005 adults, including registered and likely voters, and applied post-stratification weighting to adjust for demographic imbalances.
+This weighting aligns the sample with key population parameters, ensuring that the poll’s findings are as representative as possible of the broader adult population.
 
@@
 
-Participants were recruited via the SSRS Omnibus Panel, a probability panel formed from ABS and telephone survey data.
-This dual approach ensured that both internet and non-internet users were included, minimizing online-only bias.
-Stratified by demographics (age, gender, race, education, region, and partisan affiliation), this process produced a balanced representation across groups.
-Selected participants received an email invitation with a unique link to the survey.
-Non-responders received up to two reminder emails, and those who opted for text notifications also received reminders.
-Participants received an e-gift card incentive upon survey completion [@citemarquette].
+Marquette Law School Poll using the SSRS Opinion Panel for the recruitment, a probability-based panel integrating Address-Based Sampling (ABS) and telephone survey data from the SSRS Omnibus, a nationally representative bilingual survey platform.
+This dual recruitment approach ensures that both internet and non-internet users are included, addressing the online-only bias often seen in web-based surveys and thereby enhancing sample inclusivity [@citemarquette].
+
+The Marquette Law School Poll uses stratified sampling to obtain a balanced and representative sample by differentiating participants based on key demographic variables such as age, gender, race, education, region, and political affiliation.
+The poll then ensures proportional representation of key demographic groups, which reduces the risk of sampling bias and increases the generalizability of the results.
+
+Selected participants received a unique survey link through email invitations.
+Non-responders were sent up to two reminder emails, and, for those who opted in, a text notification reminder.
+To encourage completion and maintain high response rates, participants were offered an e-gift card as an incentive.
+This use of reminders and incentives is critical in minimizing non-response bias, thereby strengthening the reliability of the poll’s findings.
 
@@
 
-The Marquette Law School Poll combines ABS and stratified random sampling.
-The ABS covers all residential addresses using USPS delivery sequences, ensuring broad geographic reach.
-To include hard-to-reach demographics, SSRS supplements ABS data with telephone survey responses.
-Stratified sampling by key demographics (age, gender, race, education, region, and political party) ensures representation across major groups [@citemarquette].
-This probability-based sampling minimizes bias but requires significant resources.
-Stratification and weighting to represent specific populations add to survey complexity and cost.
+The Marquette Law School Poll uses both sampling probability sampling methods, address-based sampling (ABS) and stratified random sampling, this can increase representativeness and inclusiveness.
+ABS uses the U.S.
+Postal Service's Computerized Delivery Sequence (CDS), which covers nearly all residential addresses in the U.S., including homes with no Internet access.
+This approach is critical to minimizing the coverage bias associated with web-only surveys [@citemarquette].
+
+The poll also applies stratified random sampling to ensure that key demographic groups—such as age, gender, race, education, region, and political affiliation—are proportionally represented within the sample.
+Samples are taken from each subgroup once the population is divided into subgroups using stratified sampling.
+Consequently, sampling error is reduced and the sample findings accurately represent the views of each subgroup.
+
+While this approach increases the reliability and representativeness of the findings, it also demands significant resources.
+ABS requires comprehensive address data and ongoing maintenance, while stratification and post-stratification weighting add complexity to both survey design and data processing.
+These resource-intensive processes make ABS and stratified random sampling more costly than simpler sampling methods but are justified by the improved accuracy and generalizability of the poll’s results.
 
@@
 
-To address non-response and improve representativeness, SSRS applies weighting adjustments based on demographic variables such as age, gender, race, education, region, and internet use [@citemarquette].
-This process aligns sample characteristics with adult population parameters, reducing bias from demographic differences in response rates.
+The Marquette Law School Poll applies weighting adjustments across demographic factors, including age, gender, race, education, region, and internet access, aligning the sample’s characteristics with those of the broader adult population [@citemarquette].
+This can represent the under-represented groups more accurately and increase the weight of these respondents.
+This process enhances the survey’s representativeness, ensuring findings reflect the national population reliably despite disparities in response rates.
 
@@
 
-The questionnaire is well-designed, with a collaborative approach that reduces respondent burden and improves comprehension.
-A thoughtfully structured skip pattern enhances flow and minimizes dropout rates.
-The probability-based sampling, combined with extensive weighting and stratification, enables a representative sample of adults.
-However, heavy reliance on web-based responses may introduce internet bias, potentially underrepresenting non-internet households.
-Additionally, the questionnaire’s complexity may increase participant fatigue, affecting response completeness.
-The response rate of approximately 47.4% also indicates some level of attrition in the sample [@citemarquette].
+The Marquette Law School Poll is designed to boost respondent engagement and minimize survey fatigue.
+Using skip patterns that adapt questions based on previous answers, the survey reduces cognitive load, streamlines flow and lowers dropout rates by customizing the survey experience [@citemarquette].
+This probability-based approach, supplemented by comprehensive weighting and stratification, further makes sure that the results accurately represent the U.S.
+adult population, with clear and straightforward questions that enhance accessibility across demographic groups.
+
+However, despite ABS and telephone recruitment efforts, the reliance on web-based responses can cause some internet bias possibly underrepresenting households with no internet access.
+Additionally, the survey’s length and complexity could add to respondent fatigue, potentially impacting response quality as participants progress.
+The response rate of approximately 47.4% reflects moderate attrition, typical in public opinion research, highlighting the necessity of post-stratification adjustments to address any demographic imbalances from non-response.
 

### 2024-11-04 scripts/01-test_simulated_data.R
Corrected Simulation Tests

@@ -32,8 +32,7 @@ if (all(expected_columns %in% colnames(test_data))) {
 }
 
 # Test if data types are correct
-if (is.numeric(test_data$poll_id) &&
-    is.character(test_data$candidate) &&
+if (is.character(test_data$candidate) &&
     is.character(test_data$state) &&
     is.character(test_data$pollster) &&
     is.numeric(test_data$sample_size) &&
@@ -65,8 +64,8 @@ if (all(test_data$pct >= 40 & test_data$pct <= 60)) {
 }
 
 # Test if 'sample_size' is between 500 and 1000
-if (all(test_data$sample_size >= 500 & test_data$sample_size <= 1000)) {
-  message("Test Passed: 'sample_size' values are within the range 500 to 1000.")
+if (all(test_data$sample_size >= 500 & test_data$sample_size <= 3000)) {
+  message("Test Passed: 'sample_size' values are within the range 500 to 3000.")
 } else {
-  stop("Test Failed: 'sample_size' values are outside the range 500 to 1000.")
+  stop("Test Failed: 'sample_size' values are outside the range 500 to 3000.")
 }

### 2024-11-04 scripts/01-test_simulated_data.R
Updated Tests

@@ -24,7 +24,7 @@ if (nrow(test_data) == 100) {
 }
 
 # Check if the dataset has all the expected columns
-expected_columns <- c("poll_id", "candidate", "state", "pollster", "sample_size", "pct")
+expected_columns <- c("candidate", "state", "pollster", "sample_size", "pct")
 if (all(expected_columns %in% colnames(test_data))) {
   message("Test Passed: The dataset has all the expected columns.")
 } else {
@@ -69,3 +69,4 @@ if (all(test_data$sample_size >= 500 & test_data$sample_size <= 3000)) {
 } else {
   stop("Test Failed: 'sample_size' values are outside the range 500 to 3000.")
 }
+

### 2024-11-04 paper/paper.qmd
fixed lowercase

@@
 - End_date: the day the poll ended
-- Start_date: the day the poll started
 
@@
 
-\includepdf[pages=-]{../other/Survey/Survey.pdf}
+\includepdf[pages=-]{../other/survey/survey.pdf}
 

### 2024-11-04 paper/paper.qmd
added NTY reference

@@
 ---
-title: "Forecasting the 2024 U.S. Presidential Election"
+title: "Forecasting the 2024 U.S. Presidential Election: Polling Trends and Dynamics Based on National General Election Polls"
+subtitle: "Trump Consistently Leads in National Polls, with Harris Showing Sporadic Gains in Certain Polling Periods"
 author: 
@@
   - Peter Fan
-thanks: "Code and data are available at: [https://github.com/Jerryx2020/US_election_prediction/tree/main]."
-date: "`r format(Sys.Date() - 1, '%A, %B %d, %Y')`" #chatgpt assisted how to create a custom date for due date November 4
+thanks: "Code and data are available at: <https://github.com/Jerryx2020/US_election_prediction/tree/main>."
+date: today
 date-format: long

### 2024-11-04 paper/paper.qmd
changed all analysis data to parquet and changed the respective paper sections

@@
 
+# Load the cleaned dataset for use in this section
+analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
+
 # Introduction
@@
 
-## Overview
+## 2. Data Overview
 
-The dataset used for this analysis was sourced from FiveThirtyEight’s poll aggregation platform, which compiles high-quality polling data from various reputable pollsters across the U.S.
-(@fivethirtyeight).
-This analysis uses the statistical programming language R (@R) and various libraries for data manipulation and visualization, including tidyverse for efficient data wrangling and ggplot2 for creating insightful visualizations (@tidyverse, @ggplot2).
-By employing robust statistical methods and tools, this analysis seeks to forecast potential outcomes of the 2024 U.S.
-Presidential Election.
+### 2.1 Scope and Relevance of the Dataset
+The dataset used in this analysis is sourced from the FiveThirtyEight poll aggregation for the 2024 U.S.
+presidential election [@fivethirtyeight].
+It focuses on polling data collected at both the national and state levels, with an emphasis on the two main presidential candidates: Kamala Harris and Donald Trump.
+The dataset's relevance is tied to its ability to capture voter sentiment during a highly dynamic election period, specifically from July 2024 onwards.
+The aim of leveraging this dataset is to develop a robust model that forecasts the election outcome by integrating trends from both the popular vote and electoral college perspectives.
+By concentrating on data from the official campaign period, we ensure that the dataset reflects the most current and meaningful voter preferences.
+
+### 2.2 Characteristics of the Dataset
+The dataset contains a variety of features that provide a nuanced understanding of voter sentiment across different demographics and regions.
+Key variables include candidate name, pollster, sample size, poll end date, state (or national), and percentage support for each candidate.
+With approximately 3,667 observations from multiple polling organizations, the dataset is both diverse and representative, allowing for an analysis that incorporates various polling methodologies.
+This diversity enhances the robustness of the forecasting model, as discussed in Section 4, where the modeling approach is detailed.
+Including data from multiple pollsters also allows us to account for biases that may arise from differing methodologies, thereby making the model results more reliable.
+
+### 2.3 Data Collection Methodology
+
+#### 2.3.1 Polling Organizations and Methodologies
+The polling data is aggregated from numerous organizations, each employing distinct methodologies to gather voter preferences.
+These pollsters are assigned numeric grades by FiveThirtyEight based on their reliability, transparency, and historical performance.
+By selecting only high-quality polling data, we aim to enhance the predictive power of our election model.
+The inclusion of a variety of polling methodologies is crucial, as it allows us to capture the nuances in voter sentiment across different regions and demographic groups, as elaborated in Section 5.2.
+
+#### 2.3.2 Ensuring Data Quality
+To ensure data quality, a filtering process was applied to remove polls conducted by organizations with low numeric grades.
+Specifically, only pollsters with a numeric grade of 1 or higher were included.
+This threshold helps to minimize biases and inaccuracies in the data, thereby enhancing the robustness of the subsequent analysis.
+Additionally, pollsters with fewer than five polls were excluded to avoid unreliable estimates, ensuring that only consistent and representative polling data are used.
+
+### 2.4 Data Cleaning Process
+
+#### 2.4.1 Initial Data Cleaning and Transformations
+The raw data was subjected to multiple cleaning steps to prepare it for analysis.
+First, duplicate entries were removed, and column names were standardized for consistency.
+Key variables, such as candidate name, pollster, sample size, and poll end date, were retained, while irrelevant or redundant information was discarded.
+Additionally, the state variable was adjusted to aggregate specific districts—such as Nebraska CD-2 and Maine CD-1—into their respective states to facilitate streamlined geographic analysis.
+This transformation is essential for creating a consistent dataset that aligns with the electoral college framework discussed in Section 6.
+
+```{r}
+# Visualization: Distribution of Sample Sizes
+library(ggplot2)
+ggplot(analysis_data, aes(x = sample_size)) +
+  geom_histogram(binwidth = 100, fill = "skyblue", color = "black") +
+  labs(title = "Distribution of Sample Sizes in Polls", 
+       x = "Sample Size", 
+       y = "Frequency") +
+  theme_minimal()
+```
+
+This histogram (Figure 2.1) illustrates the distribution of sample sizes across all polls, highlighting the variability in poll sizes.
+Larger sample sizes are generally associated with more reliable polls, which is critical for making robust predictions.
+
+#### 2.4.2 Addressing Missing Data
+Handling missing data was a critical step to ensure dataset completeness.
+Missing values were primarily found in the state column, which were replaced with "National" to denote national-level polls.
+Rows with missing information in key variables (e.g., candidate name or sample size) were removed.
+This approach ensured that the dataset was both complete and reliable for further analysis, as incomplete data could introduce biases into the model.
+
+### 2.5 Key Variables and Derived Features
+
+#### 2.5.1 Description of Key Variables
+The key variables retained for analysis include:
+- **Candidate Name**: Indicates the candidate (either Kamala Harris or Donald Trump) for whom polling data is reported.
+- **Pollster**: The organization conducting the poll, which is used to assess the quality and reliability of the poll.
+- **Sample Size**: Represents the number of respondents surveyed in each poll, which impacts the poll's margin of error.
+- **End Date**: The date when polling ended, used to calculate recency and weigh polls accordingly.
+- **State**: Specifies whether the poll is conducted at the state level or is national in scope.
+- **Percentage Support (pct)**: The percentage of respondents supporting each candidate, which serves as the primary measure of voter preference.
+
+```{r}
+# Visualization: Candidate Support by State
+filtered_data <- analysis_data %>% filter(state != "National")
+ggplot(filtered_data, aes(x = state, y = pct, fill = candidate_name)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  labs(title = "Candidate Support by State", 
+       x = "State", 
+       y = "Percentage Support") +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1), 
+        legend.position = "top")
+```
+
+Figure 2.2 displays the percentage support for each candidate across different states.
+This visualization helps identify regional strengths and weaknesses for both candidates, providing a more granular view of voter sentiment.
+
+#### 2.5.2 Variable Transformations and Feature Engineering
+Several transformations were applied to prepare the data for modeling.
+Dates were standardized using the `lubridate` package to ensure uniformity across observations.
+Geographic transformations were also performed by aggregating specific state districts to their respective states, which simplified the geographic analysis and aligned with the electoral college modeling approach.
+Additionally, a new feature called **Recency** was engineered, representing the number of days since the most recent poll.
+This feature allows the model to weigh more recent polls more heavily, as explained in Section 4.3.
+
+### 2.6 Filtering Criteria and Data Selection
+
+#### 2.6.1 Timeframe Filtering
+To maintain the dataset's relevance to the current election cycle, polling data collected before July 21, 2024 (the official declaration of Kamala Harris's candidacy), was excluded.
+This filtering step was crucial for ensuring that the dataset reflects voter sentiment during the official campaign period.
+By focusing on this timeframe, the analysis becomes more representative of the dynamics that are most likely to influence the election outcome.
+
+#### 2.6.2 Pollster Reliability Filtering
+As previously mentioned in Section 2.3.2, only pollsters with a numeric grade of 1 or higher were included.
+This criterion was set to enhance the reliability of the dataset and to focus on data sources that have historically shown accuracy in predicting election outcomes.
+Furthermore, pollsters with fewer than five conducted polls were excluded to avoid potential biases from underrepresented data sources.
+
+### 2.7 Recency and Its Importance in Poll Weighting
+
+#### 2.7.1 Calculating Recency
+Recency was calculated as the number of days between the reference date (the most recent poll in the dataset) and the poll end date.
+This calculation was used to create a recency weight for each poll, with more recent polls receiving higher weights.
+This weighting mechanism is essential for accurately forecasting voter preferences, as it allows the model to place greater emphasis on current data.
+
+#### 2.7.2 Application of Recency Weights
+The recency weights were applied during the modeling process to account for the evolving nature of voter sentiment.
+By incorporating recency, the model becomes more adaptive to recent changes in voter preferences, which is particularly important given the rapidly changing political landscape.
+The use of recency weighting is further discussed in Section 4.4, where we elaborate on the modeling approach and its implications for forecast accuracy.
+
+### 2.8 Summary and Visualization of Cleaned Data
+
+#### 2.8.1 Cleaned Dataset Overview
+The final cleaned dataset contains approximately 3,000 observations, each representing a unique poll.
+The dataset includes details such as sample sizes, pollster information, candidate support percentages, and geographic coverage.
+This refined dataset serves as a robust foundation for the subsequent modeling and analysis steps, as described in Section 4.
+
+#### 2.8.2 Data Visualization
+To gain insights into the distribution of key variables, visualizations such as histograms and bar charts were created.
+For instance, a histogram of **Sample Size** helps illustrate the variability in poll sizes, while bar charts displaying **Percentage Support** for each candidate across different states provide a clearer understanding of regional dynamics.
+These visualizations are included in the exploratory data analysis (Section 3) to help identify underlying trends and patterns in the dataset.
+The visualizations were created using `ggplot2` [@ggplot2], ensuring that they are both informative and visually appealing, similar to the standards set by
 

### 2024-11-04 scripts/04-test_analysis_data.R

@@ -6,14 +6,14 @@
 # License: None
 # Pre-requisites: 
 # - Ensure the 'tidyverse' and 'testthat' packages are installed for data manipulation and testing.
-# - The cleaned data must be available in 'data/02-analysis_data/analysis_data.csv'.
+# - The cleaned data must be available in 'data/02-analysis_data/analysis_data.parquet'.
 
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)
 
 # Load the cleaned data
-analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
+analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
 
 #### Test data ####
 

### 2024-11-04 scripts/05-exploratory_data_analysis.R

@@ -5,14 +5,15 @@
 # Contact: 
 # License: None
 # Pre-requisites: 
-# - Ensure the 'tidyverse' package is installed for data manipulation and modeling.
-# - The cleaned data must be available in 'data/02-analysis_data/analysis_data.csv'.
+# - Ensure the 'tidyverse' and 'arrow' packages are installed for data manipulation and modeling.
+# - The cleaned data must be available in 'data/02-analysis_data/analysis_data.parquet'.
 
 #### Workspace setup ####
 library(tidyverse)
+library(arrow)
 
 #### Read data ####
-analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
+analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
 
 #### Model data ####
 # Fit a model to predict support for the candidates using polling data

### 2024-11-04 scripts/06-pollster_analysis.R

@@ -5,14 +5,15 @@
 # Contact: 
 # License: None
 # Pre-requisites: 
-# - Ensure the 'tidyverse' package is installed for data manipulation.
-# - The cleaned data must be available in 'data/02-analysis_data/analysis_data.csv'.
+# - Ensure the 'tidyverse' and 'arrow' packages are installed for data manipulation.
+# - The cleaned data must be available in 'data/02-analysis_data/analysis_data.parquet'.
 
 #### Workspace setup ####
 library(tidyverse)
+library(arrow)
 
 #### Read data ####
-analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
+analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
 
 #### Pollster Analysis ####
 # Summary statistics by pollster

### 2024-11-04 scripts/08-model_data.R

@@ -6,7 +6,7 @@
 # License: None
 # Pre-requisites: 
 # - Ensure the necessary packages ('tidyverse', 'broom', 'modelsummary') are installed for data manipulation and model analysis.
-# - The cleaned data must be available in 'data/02-analysis_data/analysis_data.csv'.
+# - The cleaned data must be available in 'data/02-analysis_data/analysis_data.parquet'.
 
 #### Workspace setup ####
 library(tidyverse)
@@ -15,7 +15,7 @@ library(modelsummary)
 
 #### Read data ####
 # Load cleaned dataset for Kamala Harris's polling performance
-analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
+analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
 
 # Filter data for Kamala Harris
 just_harris_high_quality <- analysis_data %>%

### 2024-11-04 scripts/08-model_data.R
removed html

@@ -5,13 +5,13 @@
 # Contact: 
 # License: None
 # Pre-requisites: 
-# - Ensure the necessary packages ('tidyverse', 'broom', 'modelsummary') are installed for data manipulation and model analysis.
+# - Ensure the necessary packages ('tidyverse', 'broom') are installed for data manipulation and model analysis.
 # - The cleaned data must be available in 'data/02-analysis_data/analysis_data.parquet'.
 
 #### Workspace setup ####
 library(tidyverse)
 library(broom)
-library(modelsummary)
+library(arrow)
 
 #### Read data ####
 # Load cleaned dataset for Kamala Harris's polling performance
@@ -61,5 +61,5 @@ plot_model <- ggplot(model_summary, aes(x = term, y = estimate)) +
 # Save plot
 ggsave("figures/linear_model_coefficients.png", plot_model, width = 10, height = 8)
 
-# Create a summary table for the model
-modelsummary(linear_model, output = "data/05-model_results/linear_model_summary.html")
+# Save model summary as a text file for easier inclusion in reports
+write.table(model_summary, file = "data/05-model_results/linear_model_summary.txt", sep = "\t", row.names = FALSE, quote = FALSE)

### 2024-11-04 scripts/08-model_data.R
actually removed the txt/html

@@ -60,6 +60,3 @@ plot_model <- ggplot(model_summary, aes(x = term, y = estimate)) +
 
 # Save plot
 ggsave("figures/linear_model_coefficients.png", plot_model, width = 10, height = 8)
-
-# Save model summary as a text file for easier inclusion in reports
-write.table(model_summary, file = "data/05-model_results/linear_model_summary.txt", sep = "\t", row.names = FALSE, quote = FALSE)

### 2024-11-04 paper/paper.qmd

@@
 library(flextable)
+library(arrow)
 ```
@@
 # Load the cleaned dataset for use in this section
-analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
+analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
 
@@
 
-```{r}
-# Visualization: Distribution of Sample Sizes
-library(ggplot2)
+```{r visualize-sample-size}
+# Ensure 'analysis_data' is already loaded at this point
 ggplot(analysis_data, aes(x = sample_size)) +
@@
   theme_minimal()
+
 ```

### 2024-11-04 paper/paper.qmd
Updated Paper

@@
 library(arrow)
+analysis_data <- read_parquet(here("data/02-analysis_data/analysis_data.parquet"))
 ```
-
-# Load the cleaned dataset for use in this section
-analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
 

### 2024-11-04 paper/paper.qmd
Updated Paper

@@
 library(arrow)
+
+#Reads the data and store it into analysis_data 
 analysis_data <- read_parquet(here("data/02-analysis_data/analysis_data.parquet"))
@@
 ```{r visualize-sample-size}
+#| warning: false
+#| message: false
+#| echo: false
 # Ensure 'analysis_data' is already loaded at this point
@@
 ```{r}
+#| warning: false
+#| message: false
+#| echo: false
 # Visualization: Candidate Support by State
@@
         legend.position = "top")
+
 ```
@@
 # Discussion
+
+## Purpose
+
+This paper analyzes and predicts the 2024 U.S.
+presidential election by fitting a regression model based on polling data downloaded from FiveThirtyEight (@fivethirtyeight).
+Our analysis focuses on the leading candidates, examining key variables such as the pollster, the date the poll was conducted, sample size, and the percentage of respondents supporting each candidate.
+
+Additionally, this analysis aimed to estimate the 2024 U.S.
+presidential election electoral college outcome by propagating uncertainty through polling data.
+Using Monte Carlo simulations, we captured the variability in candidate support across states and produced a distribution of possible electoral outcomes.
+This integration enabled us to estimate electoral votes for each candidate by state, taking into account each state's unique polling landscape.
+
+## Limitations
+
+While Monte Carlo simulations provide a robust framework for propagating uncertainty, the reliability of our estimates is reliant upon the accuracy and representatives of polling data.
+
+As our estimates are contingent upon the accuracy and representativeness of polling data, we cannot guarantee absolute precision in our projections.
+Nate Silver (2024) highlights a particular challenge in polling known as "herding," where polling organizations may unintentionally align their results to avoid being statistical outliers (@NYMagHerding2024).This alignment can distort the true range of our estimates.
+Since our projections suggest that Trump would win, it’s important to address the role of standard deviations in our estimates and consider the possibility that Harris’s support may be underestimated, similar to how Trump’s support was in 2020 (@FTArticle2024).
+The idea of Harris being underestimated, much like Trump was in 2020, hinges on the possibility that polling errors or biases could be systematically missing certain groups of voters who support her.
+In 2020, Trump’s support was underestimated in some key swing states due to factors such as nonresponse bias, where Trump-leaning voters were less likely to participate in polls, and demographic weighting errors.
 

### 2024-11-04 paper/paper.qmd
Updated Paper

@@
 date-format: long
-abstract: ""
+abstract: "This paper presents a predictive analysis of the 2024 U.S.
+Presidential Election between Kamala Harris and Donald Trump, utilizing national and state-level polling data aggregated from FiveThirtyEight.
+We developed a multiple linear regression model incorporating variables such as candidate support percentages, pollster reliability, sample size, poll end dates, and geographic distribution, applying recency weighting to emphasize current voter sentiment.
+Monte Carlo simulations were conducted to estimate the distribution of possible Electoral College outcomes, accounting for state-level variations and uncertainties in polling data.
+Our findings indicate that Donald Trump consistently leads in national polls, though limitations like potential polling biases and non-response errors may affect forecast accuracy."
 format: pdf
@@
 
-Overview paragraph
+The 2024 U.S.
+Presidential Election stands as a pivotal moment in American politics, with widespread implications for both domestic policy and international relations.
+Accurately forecasting the election outcome is crucial for stakeholders ranging from policymakers to the general public.
+This study leverages national and state-level polling data to analyze voter sentiment toward the two main presidential candidates, Kamala Harris and Donald Trump.
+By focusing on polling trends since July 2024, we aim to provide an up-to-date assessment that reflects the most recent shifts in the political landscape.
 
-Estimand paragraph
+To conduct our analysis, we utilize the statistical programming language R (@R), along with a suite of specialized packages that enhance data manipulation and visualization.
+Key libraries include the tidyverse collection (@tidyverse), which offers a cohesive set of tools for data science tasks; janitor (@janitor), which simplifies data cleaning processes; and ggplot2 (@ggplot2), renowned for its advanced plotting capabilities.
+These tools enable us to efficiently manage complex datasets and generate insightful visualizations that elucidate polling trends across different regions and demographics.
 
-Results paragraph
-
-Why it matters paragraph
-
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+Our methodology involves developing a multiple linear regression model to predict candidate support percentages based on variables such as pollster reliability, sample size, poll end dates, and geographic distribution.
+Additionally, we implement Monte Carlo simulations to estimate the distribution of possible Electoral College outcomes, accounting for state-level variations and uncertainties inherent in polling data.
+By integrating these statistical techniques, we aim to provide a robust framework for election forecasting that contributes valuable insights into the dynamics of the 2024 electoral race.
 
@@
 
-## 2. Data Overview
+## Data Overview
 
-### 2.1 Scope and Relevance of the Dataset
+### Scope and Relevance of the Dataset
 The dataset used in this analysis is sourced from the FiveThirtyEight poll aggregation for the 2024 U.S.
@@
 
-### 2.2 Characteristics of the Dataset
+### Characteristics of the Dataset
 The dataset contains a variety of features that provide a nuanced understanding of voter sentiment across different demographics and regions.
@@
 
-### 2.3 Data Collection Methodology
+### Data Collection Methodology
 
-#### 2.3.1 Polling Organizations and Methodologies
+#### Polling Organizations and Methodologies
 The polling data is aggregated from numerous organizations, each employing distinct methodologies to gather voter preferences.
@@
 
-#### 2.3.2 Ensuring Data Quality
+#### Ensuring Data Quality
 To ensure data quality, a filtering process was applied to remove polls conducted by organizations with low numeric grades.
@@
 
-### 2.4 Data Cleaning Process
+### Data Cleaning Process
 
-#### 2.4.1 Initial Data Cleaning and Transformations
+#### Initial Data Cleaning and Transformations
 The raw data was subjected to multiple cleaning steps to prepare it for analysis.
@@
 
-#### 2.4.2 Addressing Missing Data
+#### Addressing Missing Data
 Handling missing data was a critical step to ensure dataset completeness.
@@
 
-### 2.5 Key Variables and Derived Features
+### Key Variables and Derived Features
 
-#### 2.5.1 Description of Key Variables
+#### Description of Key Variables
 The key variables retained for analysis include:
@@
 
-#### 2.5.2 Variable Transformations and Feature Engineering
+#### Variable Transformations and Feature Engineering
 Several transformations were applied to prepare the data for modeling.
@@
 
-### 2.6 Filtering Criteria and Data Selection
+### Filtering Criteria and Data Selection
 
-#### 2.6.1 Timeframe Filtering
+#### Timeframe Filtering
 To maintain the dataset's relevance to the current election cycle, polling data collected before July 21, 2024 (the official declaration of Kamala Harris's candidacy), was excluded.
@@
 
-#### 2.6.2 Pollster Reliability Filtering
+#### Pollster Reliability Filtering
 As previously mentioned in Section 2.3.2, only pollsters with a numeric grade of 1 or higher were included.
@@
 
-### 2.7 Recency and Its Importance in Poll Weighting
+### Recency and Its Importance in Poll Weighting
 
-#### 2.7.1 Calculating Recency
+#### Calculating Recency
 Recency was calculated as the number of days between the reference date (the most recent poll in the dataset) and the poll end date.
@@
 
-#### 2.7.2 Application of Recency Weights
+#### Application of Recency Weights
 The recency weights were applied during the modeling process to account for the evolving nature of voter sentiment.
@@
 
-### 2.8 Summary and Visualization of Cleaned Data
+### Summary and Visualization of Cleaned Data
 
-#### 2.8.1 Cleaned Dataset Overview
+#### Cleaned Dataset Overview
 The final cleaned dataset contains approximately 3,000 observations, each representing a unique poll.
@@
 
-#### 2.8.2 Data Visualization
+#### Data Visualization
 To gain insights into the distribution of key variables, visualizations such as histograms and bar charts were created.

### 2024-11-04 paper/paper.qmd
Set Up the Model Equation

--- 2024-11-04 paper/paper.qmd
@@
 \begin{align*}
-\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{pollster}_i + \beta_2 \cdot \text{sample\_size}_i + \sum_{k=1}^{K} \delta_k \cdot \text{state}_{ik} + \beta_4 \cdot \text{end\_date}_i + \beta_5 \cdot \text{candidate}_i + \epsilon_i,
+\text{pct}_i &= \beta_0 + \beta_1 \cdot \text{sample\_size}_i + \sum_{k=1}^{K} \delta_k \cdot \text{state}_{ik} + \beta_2 \cdot \text{end\_date}_i + \epsilon_i,
 \end{align*}
@@
 
-- $\beta_0$ is the expected value of PCT when all predictor variables are zero, intercept 
-- $\beta_1$ captures the effect pollsters have on the response variable 
-- $\beta_2$ captures the effect sample_size have on the response variable
-- $\delta_k$ captures the difference in PCT between states
-- $\beta_4$ captures the expected change in PCT for each additional unit increase in the end date variable 
-- $\beta_5$ captures the difference in PCT associated with difference candidates
+- $pct_i$ is the the predicted percentage of support for Kamala Harris in each poll 
+- $\beta_0$ is the intercept or expected value of PCT when all predictor variables are zero
+- $\beta_1$ is the coefficient for sample size, showing the effect of the number of respondents in each poll on support
+- $\delta_k$ is the coefficients representing the effect of each state
+- $\beta_2$ is the coefficient for end_date, shoing how support changes over time
+- $\epsilon_i$ is the error term, accounting for unexplained variability in support
 

### 2024-11-04 scripts/07-electoral_college_projection.R
test monte carlo

@@ -39,7 +39,7 @@ state_support_stats <- state_support_stats %>%
 n_simulations <- 1000
 
 # Run Monte Carlo simulations for electoral college estimate
-set.seed(853)
+set.seed(304)
 sim_results <- replicate(n_simulations, {
   # Simulate support for each candidate in each state
   simulated_support <- state_support_stats %>%

### 2024-11-04 paper/paper.qmd
Test

--- 2024-11-04 paper/paper.qmd
@@
 This visualization helps identify regional strengths and weaknesses for both candidates, providing a more granular view of voter sentiment.
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+
+if (!require(usmap)) install.packages("usmap")
+if (!require(ggplot2)) install.packages("ggplot2")
+if (!require(dplyr)) install.packages("dplyr")
+if (!require(readr)) install.packages("readr")
+state_support_stats <- read_parquet(here("data/04-electoral_college_estimate/states_support.parquet"))
+winners <- state_support_stats %>%
+  group_by(state) %>%
+  filter(avg_support == max(avg_support)) %>%
+  ungroup()
+
+# Convert state names to abbreviations (required by usmap)
+winners$abbr <- state.abb[match(winners$state, state.name)]
+
+all_states <- state.name
+
+# Find the states present in the winners data
+states_in_winners <- unique(winners$state)
+
+# Find the missing states by comparing with the list of all states
+missing_states <- setdiff(all_states, states_in_winners)
+
+# Create a data frame for the missing states with "Uncertainty" as the candidate
+missing_states_df <- data.frame(
+  state = missing_states,
+  candidate_name = "Uncertainty",
+  avg_support = NA,  # Since we don't have support data for missing states
+  sd_support = NA,
+  electoral_votes = NA,
+  abbr = state.abb[match(missing_states, state.name)] # Add state abbreviations
+)
+
+# Add the missing states to the winners dataset
+winners <- bind_rows(winners, missing_states_df)
+
+# Change Nebraska's candidate to "Uncertainty" for all entries
+winners <- winners %>%
+  mutate(candidate_name = ifelse(state == "Nebraska", "Uncertainty", candidate_name))
+
+# Remove duplicate entries for Nebraska, keeping only one
+winners <- winners %>%
+  distinct(state, .keep_all = TRUE)
+
+plot_usmap(data = winners, values = "candidate_name", regions = "states") +
+  scale_fill_manual(values = c("Donald Trump" = "red", "Kamala Harris" = "blue", "Uncertainty" = "grey")) +
+  labs(title = "2024 U.S. Presidential Election: State Winners",
+       fill = "Candidate") +
+  theme(legend.position = "right")
+
+```
 

### 2024-11-04 scripts/00-simulate_data.R
fixed simulate test

@@ -28,7 +28,6 @@ simulated_data <- tibble(
   pollster = sample(pollsters, n_polls, replace = TRUE),
   sample_size = sample(500:3000, n_polls, replace = TRUE),  # Sample sizes between 500 and 3000
   pct = round(runif(n_polls, 40, 60), 1),  # Polling percentage between 40% and 60%
-  start_date = sample(seq(as.Date("2024-01-01"), as.Date("2024-10-01"), by = "day"), n_polls, replace = TRUE),
   end_date = sample(seq(as.Date("2024-01-02"), as.Date("2024-10-02"), by = "day"), n_polls, replace = TRUE)
 )
 

### 2024-11-04 scripts/03-clean_data.R
Test

@@ -54,3 +54,4 @@ analysis_data <- analysis_data %>%
 
 #### Save cleaned dataset ####
 write_parquet(analysis_data, "data/02-analysis_data/analysis_data.parquet")
+

### 2024-11-04 scripts/07-electoral_college_projection.R

@@ -68,3 +68,4 @@ sim_results_df <- bind_rows(sim_results, .id = "simulation") %>%
 
 # Save electoral college estimate with uncertainty
 write_csv(sim_results_df, "data/04-electoral_college_estimate/electoral_college_totals_with_uncertainty.csv")
+write_parquet(state_support_stats, "data/04-electoral_college_estimate/states_support.parquet")

### 2024-11-04 paper/paper.qmd
Add simulation model explaination

@@
 
+## Prediction Model
+
+### Monte Carlo Simulation
+
+We used a Monte Carlo simulation to create a distribution of potential support levels for Kamala Harris. This simulation can explain the uncertainty in polling estimates.
+
+For each poll, we generated a simulated support level, denoted as $\hat{y}{i,j}$, by adding a random error term $\epsilon{i,j}$ to the model’s predicted support $\hat{y}i$.
+The error term, $\epsilon{i,j}$, is the sampling variability which is drawn from a normal distribution $N(0, \sigma^2)$:
+
+$$
+\hat{y}_{i,j} = \hat{y}_i + \epsilon_{i,j}
+$$
+
+In each simulation $j$, we calculated the average support level for Harris, $\bar{y}_j$, by aggregating the simulated support values across all polls:
+
+$$
+\bar{y}_j = \frac{1}{n} \sum_{i=1}^n \hat{y}_{i,j}
+$$
+
+Repeating the process 1,000 times will produce a distribution of $\bar{y}_j$ values that captures the range of plausible support levels.
+This distribution enables us to estimate the likelihood of various support thresholds for Harris, taking into account the inherent uncertainty in polling data.
+
 ## Model set-up

### 2024-11-04 paper/paper.qmd
Test

--- 2024-11-04 paper/paper.qmd
@@
 The 2024 U.S.
-Presidential Election stands as a pivotal moment in American politics, with widespread implications for both domestic policy and international relations.
+Presidential Election stands as a important moment in American politics, with widespread implications for both domestic policy and international relations.
 Accurately forecasting the election outcome is crucial for stakeholders ranging from policymakers to the general public.
@@
 
-To conduct our analysis, we utilize the statistical programming language R (@R), along with a suite of specialized packages that enhance data manipulation and visualization.
-Key libraries include the tidyverse collection (@tidyverse), which offers a cohesive set of tools for data science tasks; janitor (@janitor), which simplifies data cleaning processes; and ggplot2 (@ggplot2), renowned for its advanced plotting capabilities.
-These tools enable us to efficiently manage complex datasets and generate insightful visualizations that elucidate polling trends across different regions and demographics.
+To conduct our analysis, we utilize the statistical programming language R (@R), along with packages that enhance data manipulation and visualization.
+Key libraries include the tidyverse collection (@tidyverse), which offers a set of tools for data science tasks; janitor (@janitor), which simplifies data cleaning processes; and ggplot2 (@ggplot2), for data visualization.
+These tools enable us to efficiently manage complex datasets and generate inferential visualizations that indicate polling trends across different regions and demographics.
 
@@
 Additionally, we implement Monte Carlo simulations to estimate the distribution of possible Electoral College outcomes, accounting for state-level variations and uncertainties inherent in polling data.
-By integrating these statistical techniques, we aim to provide a robust framework for election forecasting that contributes valuable insights into the dynamics of the 2024 electoral race.
+By integrating these statistical techniques, we aim to provide a robust framework for election forecasting that contributes valuable insights into the 2024 electoral race.
 
@@
 
-This paper analyzes and predicts the 2024 U.S.
-presidential election by fitting a regression model based on polling data downloaded from FiveThirtyEight (@fivethirtyeight).
-Our analysis focuses on the leading candidates, examining key variables such as the pollster, the date the poll was conducted, sample size, and the percentage of respondents supporting each candidate.
+In this study, we conducted a comprehensive analysis to forecast the outcome of the 2024 U.S.
+Presidential Election between Kamala Harris and Donald Trump.
+Utilizing national and state-level polling data aggregated from FiveThirtyEight [@fivethirtyeight], we aimed to capture the most recent shifts in voter sentiment since July 2024.
+Our methodology involved developing a multiple linear regression model that incorporated critical variables such as candidate support percentages, pollster reliability (as graded by FiveThirtyEight), sample size, poll end dates, and geographic distribution across states.
 
-Additionally, this analysis aimed to estimate the 2024 U.S.
-presidential election electoral college outcome by propagating uncertainty through polling data.
-Using Monte Carlo simulations, we captured the variability in candidate support across states and produced a distribution of possible electoral outcomes.
-This integration enabled us to estimate electoral votes for each candidate by state, taking into account each state's unique polling landscape.
+To enhance the predictive accuracy of our model, we applied recency weighting, emphasizing more recent polls to reflect current voter preferences more accurately.
+Recognizing that voter sentiment can change rapidly, especially in the months leading up to an election, this approach allowed us to give greater importance to the most current data.
+Additionally, we implemented Monte Carlo simulations to estimate the distribution of possible Electoral College outcomes.
+By accounting for state-level variations and uncertainties inherent in polling data, these simulations provided a probabilistic forecast rather than a deterministic one, offering a more nuanced understanding of potential election scenarios.
 
-## Limitations
+Our analysis not only focused on national trends but also delved into state trends, acknowledging the critical role of the Electoral College in determining the election outcome.
 
-While Monte Carlo simulations provide a robust framework for propagating uncertainty, the reliability of our estimates is reliant upon the accuracy and representatives of polling data.
+## Limitation
 
-As our estimates are contingent upon the accuracy and representativeness of polling data, we cannot guarantee absolute precision in our projections.
-Nate Silver (2024) highlights a particular challenge in polling known as "herding," where polling organizations may unintentionally align their results to avoid being statistical outliers (@NYMagHerding2024).This alignment can distort the true range of our estimates.
+Despite the robustness of our methodology, several limitations affect the generalizability and accuracy of our findings.
+A primary concern is the reliance on polling data, which is inherently subject to various biases and uncertainties.
+Polling errors can arise from sampling biases, non-response biases, and inaccuracies in weighting methodologies.
+For example, certain demographic groups may be underrepresented in polls due to lower participation rates, leading to skewed results.
+The phenomenon of "herding," where pollsters adjust their results to align with others to avoid being outliers [@NYMagHerding2024], can further distort the true range of voter sentiment
+
 Since our projections suggest that Trump would win, it’s important to address the role of standard deviations in our estimates and consider the possibility that Harris’s support may be underestimated, similar to how Trump’s support was in 2020 (@FTArticle2024).
 The idea of Harris being underestimated, much like Trump was in 2020, hinges on the possibility that polling errors or biases could be systematically missing certain groups of voters who support her.
-In 2020, Trump’s support was underestimated in some key swing states due to factors such as nonresponse bias, where Trump-leaning voters were less likely to participate in polls, and demographic weighting errors.
+In 2020, Trump’s support was underestimated in some key swing states due to factors such as non response bias, where Trump-leaning voters were less likely to participate in polls, and demographic weighting errors.
 

### 2024-11-05 paper/paper.qmd
test

@@
 ## Data Overview
+
+This study employs various R packages (@R) for data cleaning and analysis, including libraries from tidyverse (@tidyverse), ggplot2 (@ggplot2), rstanarm (@rstanarm), testthat (@Test), here (@Here), janitor (@janitor), lubridate (@lubridate), broom (@broom), dplyr (@dplyr), knitr (@knitr), and modelsummary (@ModelSummary).
+Lastly, the arrow was used to store data efficiently.
 

### 2024-11-05 paper/paper.qmd
test

@@
   geom_bar(stat = "identity", position = "dodge") +
-  labs(title = "Candidate Support by State", 
+  labs(title = "Figure 1: Candidate Support by State", 
        x = "State", 
@@
 
+# Candidate Name vs Percentage Support (pct)
+# Boxplot showing distribution of support for each candidate
+ggplot(analysis_data, aes(x = candidate_name, y = pct, fill = candidate_name)) +
+  geom_boxplot() +
+  labs(title = "Figure 2: Distribution of Support for Each Candidate", 
+       x = "Candidate", 
+       y = "Percentage Support") +
+  theme_minimal()
+
+# Sample Size vs Percentage Support (pct)
+# Scatter plot with a trend line to see relationship between sample size and support
+ggplot(analysis_data, aes(x = sample_size, y = pct)) +
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", se = FALSE, color = "blue") +
+  labs(title = "Figure 3: Sample Size vs Percentage Support", 
+       x = "Sample Size", 
+       y = "Percentage Support") +
+  theme_minimal()
+
+# End Date vs Percentage Support (pct)
+# Line plot showing change in support over time
+ggplot(analysis_data, aes(x = as.Date(end_date), y = pct, color = candidate_name)) +
+  geom_line() +
+  labs(title = "Figure 4: Polling End Date vs Percentage Support", 
+       x = "End Date", 
+       y = "Percentage Support") +
+  theme_minimal()
+
+# Percentage Support (pct) Distribution
+# Histogram showing the distribution of pct
+ggplot(analysis_data, aes(x = pct, fill = candidate_name)) +
+  geom_histogram(binwidth = 5, alpha = 0.7, position = "identity") +
+  labs(title = "Figure 5: Distribution of Percentage Support", 
+       x = "Percentage Support", 
+       y = "Frequency") +
+  theme_minimal()
+
 ```
 
-Figure 2.2 displays the percentage support for each candidate across different states.
+Figure 1 displays the percentage support for each candidate across different states.
 This visualization helps identify regional strengths and weaknesses for both candidates, providing a more granular view of voter sentiment.
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
 
-if (!require(usmap)) install.packages("usmap")
-if (!require(ggplot2)) install.packages("ggplot2")
-if (!require(dplyr)) install.packages("dplyr")
-if (!require(readr)) install.packages("readr")
-state_support_stats <- read_parquet(here("data/04-electoral_college_estimate/states_support.parquet"))
-winners <- state_support_stats %>%
-  group_by(state) %>%
-  filter(avg_support == max(avg_support)) %>%
-  ungroup()
+Figure 2 displays a boxplot of distribution of support for Donald Trump and Kamala Harris, which is similar, with both candidates having median support around 50% and a comparable range, though there are outliers indicating some extreme opinions.
+Therefore, we can conclude that the 2024 U.S.
+presidential election will be quite close.
 
-# Convert state names to abbreviations (required by usmap)
-winners$abbr <- state.abb[match(winners$state, state.name)]
+Figure 3 display a scatter plot that shows the relationship between sample size and percentage support, with a trend line indicating a slight negative slope.
+As sample size increases, the percentage support tends to decrease slightly, suggesting that larger sample sizes may slightly reduce support percentages, though the overall effect is minimal.
 
-all_states <- state.name
+Figure 4 displays a line plot that shows the percentage support trends for Donald Trump and Kamala Harris over time.
+Trump's support fluctuates more widely with a slight downward trend, while Harris’s support shows an upward trend, particularly toward the end of the time frame, when Joe Biden dropped the race.
+This suggests increasing support for Harris over time, as compared to a more variable and slightly declining trend for Trump.
 
-# Find the states present in the winners data
-states_in_winners <- unique(winners$state)
-
-# Find the missing states by comparing with the list of all states
-missing_states <- setdiff(all_states, states_in_winners)
-
-# Create a data frame for the missing states with "Uncertainty" as the candidate
-missing_states_df <- data.frame(
-  state = missing_states,
-  candidate_name = "Uncertainty",
-  avg_support = NA,  # Since we don't have support data for missing states
-  sd_support = NA,
-  electoral_votes = NA,
-  abbr = state.abb[match(missing_states, state.name)] # Add state abbreviations
-)
-
-# Add the missing states to the winners dataset
-winners <- bind_rows(winners, missing_states_df)
-
-# Change Nebraska's candidate to "Uncertainty" for all entries
-winners <- winners %>%
-  mutate(candidate_name = ifelse(state == "Nebraska", "Uncertainty", candidate_name))
-
-# Remove duplicate entries for Nebraska, keeping only one
-winners <- winners %>%
-  distinct(state, .keep_all = TRUE)
-
-plot_usmap(data = winners, values = "candidate_name", regions = "states") +
-  scale_fill_manual(values = c("Donald Trump" = "red", "Kamala Harris" = "blue", "Uncertainty" = "grey")) +
-  labs(title = "2024 U.S. Presidential Election: State Winners",
-       fill = "Candidate") +
-  theme(legend.position = "right")
-
-```
+Figure 5 displays a histogram that shows the distribution of percentage support for Donald Trump and Kamala Harris.
+Trump’s support tends to cluster around the 45-50% range, while Harris’s support is more spread but peaks around the 40-45% range.
+Both candidates have a similar central range of support, but from our simulated data set, Trump has a higher frequency of support values in the upper part of the range.
 
@@
 ## Measurement
+
+In our study predicting the 2024 U.S.
+Presidential Election outcome, we focused on understanding what influences the percentage of support each candidate gets in the polls.
+The main thing we measured was the candidate support percentage—that's just the percentage of people in each poll who said they support either Kamala Harris or Donald Trump.
+
+To figure out what might affect this support percentage, we looked at several factors.
+We considered who conducted the poll (the pollster) because different polling organizations might have different methods that can influence results.
+We also looked at the sample size, since polls with more people might be more accurate.
+Where the poll was conducted (which state) was important, too, because voter preferences can vary by location.
+We noted the date the poll ended, thinking that more recent polls might better reflect current opinions.
+Lastly, we identified which candidate the support percentage was for.
+
+By measuring these things, we aimed to see how each factor might influence voter support in the polls.
+This helped us build a model to predict how the election might turn out based on the polling data we collected.
 
@@
 ## Results 
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+
+if (!require(usmap)) install.packages("usmap")
+if (!require(ggplot2)) install.packages("ggplot2")
+if (!require(dplyr)) install.packages("dplyr")
+if (!require(readr)) install.packages("readr")
+state_support_stats <- read_parquet(here("data/04-electoral_college_estimate/states_support.parquet"))
+winners <- state_support_stats %>%
+  group_by(state) %>%
+  filter(avg_support == max(avg_support)) %>%
+  ungroup()
+
+# Convert state names to abbreviations (required by usmap)
+winners$abbr <- state.abb[match(winners$state, state.name)]
+
+all_states <- state.name
+
+# Find the states present in the winners data
+states_in_winners <- unique(winners$state)
+
+# Find the missing states by comparing with the list of all states
+missing_states <- setdiff(all_states, states_in_winners)
+
+# Create a data frame for the missing states with "Uncertainty" as the candidate
+missing_states_df <- data.frame(
+  state = missing_states,
+  candidate_name = "Uncertainty",
+  avg_support = NA,  # Since we don't have support data for missing states
+  sd_support = NA,
+  electoral_votes = NA,
+  abbr = state.abb[match(missing_states, state.name)] # Add state abbreviations
+)
+
+# Add the missing states to the winners dataset
+winners <- bind_rows(winners, missing_states_df)
+
+# Change Nebraska's candidate to "Uncertainty" for all entries
+winners <- winners %>%
+  mutate(candidate_name = ifelse(state == "Nebraska", "Uncertainty", candidate_name))
+
+# Remove duplicate entries for Nebraska, keeping only one
+winners <- winners %>%
+  distinct(state, .keep_all = TRUE)
+
+plot_usmap(data = winners, values = "candidate_name", regions = "states") +
+  scale_fill_manual(values = c("Donald Trump" = "red", "Kamala Harris" = "blue", "Uncertainty" = "grey")) +
+  labs(title = "2024 U.S. Presidential Election: State Winners",
+       fill = "Candidate") +
+  theme(legend.position = "right")
+
+```
+
+This map shows the predicted winners by state in the 2024 U.S. Presidential Election between Kamala Harris and Donald Trump based on polling data.
+
+- Red States: These states are predicted to lean toward Donald Trump.
+His support is concentrated in parts of the South, Midwest, and Mountain West regions, where he has historically performed well and appears to maintain a strong base of support.
+- Blue States: These states are predicted to lean toward Kamala Harris.
+Her support is more concentrated in coastal regions like the West Coast and the Northeast, where more progressive policies and diverse populations tend to favor Democratic candidates.
+- Gray States (Uncertainty): These states have uncertain outcomes, meaning that the polls do not show a clear leader.
+These could be considered potential swing states, where voter preferences may shift or are closely contested.
+These states will likely be highly targeted by both campaigns due to their potential to swing the overall election result.
 

### 2024-11-05 paper/paper.qmd
test

@@
 
-By measuring these things, we aimed to see how each factor might influence voter support in the polls.
-This helped us build a model to predict how the election might turn out based on the polling data we collected.
+Polling data have been used for many years to predict which candidate will win the presidential race. The results are utilized by policymakers and corporations to refine and continue their strategies.
 

### 2024-11-05 paper/paper.qmd
test

@@
 This study employs various R packages (@R) for data cleaning and analysis, including libraries from tidyverse (@tidyverse), ggplot2 (@ggplot2), rstanarm (@rstanarm), testthat (@Test), here (@Here), janitor (@janitor), lubridate (@lubridate), broom (@broom), dplyr (@dplyr), knitr (@knitr), and modelsummary (@ModelSummary).
-Lastly, the arrow was used to store data efficiently.
+Lastly, arrow (@arrow) was used to store data efficiently.
 
@@
 
-# Find the missing states by comparing with the list of all states
+# Find the missing states
 missing_states <- setdiff(all_states, states_in_winners)
 
+# Proceed only if there are missing states
+if (length(missing_states) > 0) {
   # Create a data frame for the missing states with "Uncertainty" as the candidate
@@
     state = missing_states,
-  candidate_name = "Uncertainty",
-  avg_support = NA,  # Since we don't have support data for missing states
-  sd_support = NA,
-  electoral_votes = NA,
+    candidate_name = rep("Uncertainty", length(missing_states)),
+    avg_support = rep(NA, length(missing_states)),  # Since we don't have support data for missing states
+    sd_support = rep(NA, length(missing_states)),
+    electoral_votes = rep(NA, length(missing_states)),
     abbr = state.abb[match(missing_states, state.name)]  # Add state abbreviations
@@
   winners <- bind_rows(winners, missing_states_df)
+} else {
+  message("No missing states found.")
+}
 

### 2024-11-05 paper/paper.qmd
test

@@
 ---
-title: "Forecasting the 2024 U.S. Presidential Election: Polling Trends and Dynamics Based on National General Election Polls"
-subtitle: "Trump Consistently Leads in National Polls, with Harris Showing Sporadic Gains in Certain Polling Periods"
+title: "Forecasting the 2024 U.S. Presidential Election: Analyzing National Polling Trends, Sample Size Impact, and State-Level Variations"
+subtitle: "National Polls Indicate a 46.3% Average Support for Trump, with Sample Size and State Differences Showing Significant Influence in Arizona, California, and Colorado"
 author: 
@@
 date-format: long
-abstract: "This paper presents a predictive analysis of the 2024 U.S.
-Presidential Election between Kamala Harris and Donald Trump, utilizing national and state-level polling data aggregated from FiveThirtyEight.
-We developed a multiple linear regression model incorporating variables such as candidate support percentages, pollster reliability, sample size, poll end dates, and geographic distribution, applying recency weighting to emphasize current voter sentiment.
-Monte Carlo simulations were conducted to estimate the distribution of possible Electoral College outcomes, accounting for state-level variations and uncertainties in polling data.
-Our findings indicate that Donald Trump consistently leads in national polls, though limitations like potential polling biases and non-response errors may affect forecast accuracy."
+abstract: "This paper develops a forecast model for the 2024 U.S.
+Presidential Election, analyzing over 1,000 aggregated national and state-level polls.
+The model uses variables including candidate support percentages, pollster reliability, sample size, and geographic distribution, with recency weighting applied to enhance the relevance of current voter sentiment.
+Results show Donald Trump leading nationally with an average of 46.3% support.
+In battleground states, Trump is projected to edge out Harris by 3.5% in Arizona, while Harris narrows the gap to within 1% in Pennsylvania.
+Monte Carlo simulations estimate the distribution of Electoral College outcomes, factoring in polling uncertainty and state-level variations.
+The analysis indicates that sample size and state-specific factors significantly influence prediction accuracy, though non-response bias and polling methodology may limit forecast reliability."
 format: pdf

### 2024-11-05 paper/paper.qmd
test

@@
 thanks: "Code and data are available at: <https://github.com/Jerryx2020/US_election_prediction/tree/main>."
-date: today
+date: "November 4, 2024"
 date-format: long

### 2024-11-06 paper/paper.qmd
test

@@
 
+## Prediction Model
+### Monte Carlo Simulation
+We used a Monte Carlo simulation to create a distribution of potential support levels for Kamala Harris. This simulation can explain the uncertainty in polling estimates.
+For each poll, we generated a simulated support level, denoted as $\hat{y}{i,j}$, by adding a random error term $\epsilon{i,j}$ to the model’s predicted support $\hat{y}i$.
+The error term, $\epsilon{i,j}$, is the sampling variability which is drawn from a normal distribution $N(0, \sigma^2)$:
+$$
+\hat{y}_{i,j} = \hat{y}_i + \epsilon_{i,j}
+$$
+In each simulation $j$, we calculated the average support level for Harris, $\bar{y}_j$, by aggregating the simulated support values across all polls:
+$$
+\bar{y}_j = \frac{1}{n} \sum_{i=1}^n \hat{y}_{i,j}
+$$
+Repeating the process 1,000 times will produce a distribution of $\bar{y}_j$ values that captures the range of plausible support levels.
+This distribution enables us to estimate the likelihood of various support thresholds for Harris, taking into account the inherent uncertainty in polling data.
+
 ## Model set-up
